\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{xcolor}
% % \usepackage{tikz}
% % \usetikzlibrary{shapes.geometric, arrows, positioning}
\usepackage{amsmath}
\usepackage{longtable}

% Color definitions for code blocks
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

% Code snippet styling config
\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle={\small\ttfamily},
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}
\lstset{style=mystyle}

% Flowchart styles
% % \tikzstyle{startstop} = [rectangle, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=red!30]
% % \tikzstyle{io} = [trapezium, trapezium left angle=70, trapezium right angle=110, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=blue!30]
% % \tikzstyle{process} = [rectangle, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=orange!30]
% % \tikzstyle{decision} = [diamond, minimum width=3.5cm, minimum height=1cm, text centered, draw=black, fill=green!30]
% % \tikzstyle{arrow} = [thick,->,>=stealth]

\title{MicroJava Mini-Compiler Project \\ \large Comprehensive Architectural Flow, Component Linkage, and Implementation Report}
\author{ESA irfan (2023-cs-104) \and Hamdan Aleem (2023-cs-107) \\
\vspace{0.3cm} \\
Department of Computer Science \\
University of Engineering and Technology (UET), Lahore \\
\vspace{0.5cm} \\
Instructor: Ms. Aaliya}
\date{\today}

\begin{document}

\maketitle

\newpage
\begin{abstract}
This report details the design and implementation of a multi-stage syntax validator and execution engine for the MicroJava language. The compiler incorporates five core phases: double-buffered lexical analysis, recursive descent parsing with dynamic ASCII tree visualization, chained-scope symbol table management, LL(1) non-recursive predictive parsing using an explicit stack, and Canonical LR(1) bottom-up parsing. We explore grammar transformations required to resolve left recursion and left factoring for LL(1) predictive parsing. We also justify the choice of Canonical LR(1) for bottom-up parsing and present end-to-end execution traces mapping input source code through every compilation compiler layer.
\end{abstract}

\newpage
\tableofcontents
\newpage

\section{Introduction and Language Overview}
\subsection{Introduction to MicroJava}
MicroJava is a subset of Java designed for compiler construction courses. It is a strongly-typed, object-oriented language that supports basic data types (integers and characters), constants, arrays, static class-like structures, methods, nested scopes, and control flow statements (such as conditional execution and loops). 

\subsection{Key Implementation Features}
The compiler implementation described in this report incorporates the following architectural highlights:
\begin{itemize}
    \item \textbf{C++17 Compiler Core}: Highly performant binary execution layer supporting five synchronized analysis phases.
    \item \textbf{Single-Error Termination}: In compliance with robust validator rules, all three parser engines stop execution immediately at the first lexical, syntax, or semantic error, preventing cascading errors.
    \item \textbf{Visual Representation}: The Recursive Descent parser outputs a colored ASCII concrete tree illustrating exact scope nesting and grammar expansions.
\end{itemize}



\section{Compiler Project Code Files and Linkage}
The project consists of multiple header files, C++ source modules, Python scripts, and frontend assets. They are linked together logically to form the compiler suite.

\newpage

\section{MicroJava EBNF Grammar Specification}
The parser expects code written in accordance with the Context-Free Grammar (CFG) rules below:

\begin{lstlisting}[language=HTML, caption=MicroJava EBNF Grammar]
Program = "program" ident {ConstDecl | VarDecl | ClassDecl} "{" {MethodDecl} "}".
ConstDecl = "final" Type ident "=" (number | charConst) ";".
VarDecl = Type ident {"," ident} ";".
ClassDecl = "class" ident "{" {VarDecl} "}".
MethodDecl = (Type | "void") ident "(" [FormPars] ")" {VarDecl} Block.
FormPars = Type ident {"," Type ident}.
Type = ident ["[" "]"].
Block = "{" {Statement} "}".
Statement = Designator ("=" Expr | ActPars) ";"
          | "if" "(" Condition ")" Statement ["else" Statement]
          | "while" "(" Condition ")" Statement
          | "return" [Expr] ";"
          | "read" "(" Designator ")" ";"
          | "print" "(" Expr ["," number] ")" ";"
          | Block
          | ";".
ActPars = "(" [Expr {"," Expr}] ")".
Condition = Expr Relop Expr.
Relop = "==" | "!=" | ">" | ">=" | "<" | "<=".
Expr = ["-"] Term {Addop Term}.
Addop = "+" | "-".
Term = Factor {Mulop Factor}.
Mulop = "*" | "/" | "%".
Factor = Designator [ActPars]
       | number
       | charConst
       | "new" ident ["[" Expr "]"]
       | "(" Expr ")".
Designator = ident {"." ident | "[" Expr "]"}.
\end{lstlisting}

\subsection{Left Recursion and Left Factoring Solutions}
To build a top-down parser like LL(1) or Recursive Descent, the grammar must be free from:
\begin{enumerate}
    \item \textbf{Left Recursion}: Rules like $A \rightarrow A\,\alpha \mid \beta$ cause infinite recursion.
    \item \textbf{Common Prefixes}: Rules like $A \rightarrow \alpha\,\beta_1 \mid \alpha\,\beta_2$ prevent deterministic lookahead.
\end{enumerate}

\subsubsection{Left Recursion Solution}
We eliminate direct left recursion using the transformation:
$$A \rightarrow A\,\alpha \mid \beta \quad \Longrightarrow \quad A \rightarrow \beta\,A' \quad \text{and} \quad A' \rightarrow \alpha\,A' \mid \epsilon$$
*Example Application (Expression rules)*:
Original expression grammar:
$$\text{Expr} \rightarrow \text{Expr} \,\, \text{Addop} \,\, \text{Term} \mid \text{Term}$$
We transform this into:
$$\text{Expr} \rightarrow \text{Term} \,\, \text{Expr'}$$
$$\text{Expr'} \rightarrow \text{Addop} \,\, \text{Term} \,\, \text{Expr'} \mid \epsilon$$

\subsubsection{Left Factoring Solution}
Where rules share a common prefix, we delay the decision by moving the factor out:
$$A \rightarrow \alpha\,\beta_1 \mid \alpha\,\beta_2 \quad \Longrightarrow \quad A \rightarrow \alpha\,A' \quad \text{and} \quad A' \rightarrow \beta_1 \mid \beta_2$$
*Example Application (Designator Tail)*:
$$\text{Designator} \rightarrow \text{ident} \cdot \text{ident} \mid \text{ident} \, [ \text{Expr} ] \mid \text{ident}$$
We factor out $\text{ident}$:
$$\text{Designator} \rightarrow \text{ident} \,\, \text{Designator\_Tail}$$
$$\text{Designator\_Tail} \rightarrow \text{.} \, \text{ident} \, \text{Designator\_Tail} \mid \text{[} \, \text{Expr} \, \text{]} \, \text{Designator\_Tail} \mid \epsilon$$

\subsection{Full Transformed LL(1) Grammar}
Below is the complete, transformed MicroJava grammar after removing all left recursions and applying left factoring:
\begin{lstlisting}[language=HTML, caption=Full Transformed LL(1) Grammar]
Program = "program" ident Program_Body "{" MethodDecls "}".
Program_Body = {ConstDecl | VarDecl | ClassDecl}.
ConstDecl = "final" Type ident "=" ConstValue ";".
ConstValue = number | charConst.
VarDecl = Type ident VarDecl_Tail ";".
VarDecl_Tail = {"," ident}.
ClassDecl = "class" ident "{" VarDecls "}".
VarDecls = {VarDecl}.
MethodDecls = {MethodDecl}.
MethodDecl = MethodType ident "(" FormPars_Opt ")" VarDecls Block.
MethodType = Type | "void".
FormPars_Opt = [FormPars].
FormPars = Type ident FormPars_Tail.
FormPars_Tail = {"," Type ident}.
Type = ident Type_Opt.
Type_Opt = ["[" "]"].
Block = "{" Statements "}".
Statements = {Statement}.
Statement = Designator Statement_AssignOrCall ";"
          | "if" "(" Condition ")" Statement Else_Opt
          | "while" "(" Condition ")" Statement
          | "return" Expr_Opt ";"
          | "read" "(" Designator ")" ";"
          | "print" "(" Expr Print_Opt ")" ";"
          | Block
          | ";".
Statement_AssignOrCall = "=" Expr | ActPars.
Else_Opt = ["else" Statement].
Expr_Opt = [Expr].
Print_Opt = ["," number].
ActPars = "(" ActPars_List ")".
ActPars_List = [Expr ActPars_Tail].
ActPars_Tail = {"," Expr}.
Condition = Expr Relop Expr.
Relop = "==" | "!=" | ">" | ">=" | "<" | "<=".
Expr = Expr_Minus Term Expr_Tail.
Expr_Minus = ["-"].
Expr_Tail = {Addop Term}.
Addop = "+" | "-".
Term = Factor Term_Tail.
Term_Tail = {Mulop Factor}.
Mulop = "*" | "/" | "%".
Factor = Designator Factor_Designator
       | number
       | charConst
       | "new" ident Factor_New
       | "(" Expr ")".
Factor_Designator = [ActPars].
Factor_New = ["[" Expr "]"].
Designator = ident Designator_Tail.
Designator_Tail = {"." ident | "[" Expr "]"}.
\end{lstlisting}

\newpage

\section{Theoretical Logic and Implementation details}

\subsection{Lexical Analyzer (Lexer)}
\subsubsection{Theoretical Logic}
The lexer converts a sequence of characters into a sequence of tokens. It reads characters from a file stream and partitions them based on the regular definitions of the vocabulary:
\begin{itemize}
    \item $\text{Keyword} = \textbf{program} \mid \textbf{class} \mid \textbf{void} \mid \textbf{final} \mid \textbf{new} \mid \textbf{if} \mid \textbf{else} \mid \textbf{while} \mid \textbf{read} \mid \textbf{print} \mid \textbf{return}$
    \item $\text{Identifier} = \text{letter} \, (\text{letter} \mid \text{digit})^*$
    \item $\text{Number} = \text{digit}^+$
    \item $\text{CharConst} = \text{'`'} \, \text{any\_printable\_char} \, \text{'`'}$
\end{itemize}
It uses a double-buffering scheme to process characters efficiently and keeps track of character coordinates (line and column numbers) to pinpoint lexical errors.

\subsection{Recursive Descent Parser \& Tree Logic}
\subsubsection{Theoretical Logic}
The Recursive Descent (RD) parser is a top-down validation system. It matches the sequence of tokens by recursively calling parsing functions corresponding to each non-terminal. 

\subsubsection{Tree Generation Logic}
The parser outputs a text-based representation of the Concrete Syntax Tree (CST) by tracking the call stack depth using a nesting counter variable:
\begin{itemize}
    \item When a parsing function (e.g., `parseVarDecl()`) is entered, `indentLevel` is incremented.
    \item A branch node name is printed prefixed by vertical lines ($\text{indentLevel} \times \text{``│ ''}$).
    \item When the function returns, `indentLevel` is decremented.
\end{itemize}
Because this tree corresponds exactly to the parser's active execution stack, it represents the leftmost derivation hierarchy of the program.

\subsection{Non-Recursive LL(1) Stack Parser}
\subsubsection{Theoretical Logic}
Unlike recursive descent, the LL(1) parser uses a non-recursive predictive parsing model with an explicit stack. It looks up transitions in the 2D parser table $M[A, a]$:
\begin{itemize}
    \item If the top of the stack is a terminal and matches the lookahead token, it pops and advances.
    \item If the top is a non-terminal $A$, it queries the table $M[A, a]$ to retrieve rule $A \rightarrow Y_1 Y_2 \dots Y_k$. It pops $A$ and pushes the right-hand symbols onto the stack in reverse order: $Y_k$, then $Y_{k-1}$ down to $Y_1$.
\end{itemize}

\subsection{Canonical LR(1) Parser}
\subsubsection{Theoretical Logic and Choice Justification}
The LR(1) parser is a bottom-up shift-reduce syntax validator. We chose the **Canonical LR(1)** model for our bottom-up parser. 

\subsubsection{Justification for Canonical LR(1)}
We preferred Canonical LR(1) over LR(0), SLR(1), or LALR(1) due to the following reasons:
\begin{enumerate}
    \item \textbf{Explicit Lookahead handling}: LR(1) embeds lookahead items $[A \rightarrow \alpha \cdot \beta, a]$ directly within states, resolving shift/reduce conflicts that SLR(1) cannot handle due to its reliance on FOLLOW sets.
    \item \textbf{No Conflict Merging}: Unlike LALR(1), which merges states with the same core items but different lookaheads (sometimes introducing reduce-reduce conflicts), Canonical LR(1) keeps these states split, guaranteeing strict parsing correctness.
    \item \textbf{Handles Complex Subsets}: MicroJava contains nested expression boundaries and variable scopes where shift-reduce decisions depend heavily on the lookahead. LR(1) guarantees unambiguous transitions.
\end{enumerate}

\subsubsection{Standard Shift-Reduce Algorithm}
The parser maintains a stack of states $s_0 s_1 \dots s_m$ and a stack of symbols $X_1 X_2 \dots X_m$. 
For each step, let $s$ be the state at the top of the stack, and $a$ be the current lookahead token. It queries $\text{Action}[s, a]$:
\begin{enumerate}
    \item \textbf{Shift to state $s'$}: Push $a$ onto the symbol stack, push $s'$ onto the state stack, and fetch the next token.
    \item \textbf{Reduce by rule $A \rightarrow \beta$}: Pop $r = |\beta|$ symbols and states off the stacks. Let the new top state be $s''$. Query the GOTO table entry $s_{new} = \text{Goto}[s'', A]$. Push symbol $A$ and state $s_{new}$ onto the stacks.
    \item \textbf{Accept}: Terminate parsing with success.
    \item \textbf{Error}: Stop parsing immediately and print the line and column numbers.
\end{enumerate}

\newpage

\section{Grammar Parsing Sets and Representative Tables}

\subsection{FIRST Sets}
\begin{center}
\begin{tabular}{|l|p{10cm}|}
\hline
\textbf{Non-Terminal} & \textbf{FIRST Set} \\ \hline
\texttt{ActPars} & \texttt{(} \\ \hline
\texttt{ActPars\_List} & $\epsilon$, \texttt{(}, \texttt{-}, \texttt{charConst}, \texttt{ident}, \texttt{new}, \texttt{number} \\ \hline
\texttt{ActPars\_Tail} & $\epsilon$, \texttt{,} \\ \hline
\texttt{Addop} & \texttt{+}, \texttt{-} \\ \hline
\texttt{Block} & \texttt{\{} \\ \hline
\texttt{ClassDecl} & \texttt{class} \\ \hline
\texttt{Condition} & \texttt{(}, \texttt{-}, \texttt{charConst}, \texttt{ident}, \texttt{new}, \texttt{number} \\ \hline
\texttt{ConstDecl} & \texttt{final} \\ \hline
\texttt{ConstValue} & \texttt{charConst}, \texttt{number} \\ \hline
\texttt{Designator} & \texttt{ident} \\ \hline
\texttt{Designator\_Tail} & $\epsilon$, \texttt{.}, \texttt{[} \\ \hline
\texttt{Else\_Opt} & $\epsilon$, \texttt{else} \\ \hline
\texttt{Expr} & \texttt{(}, \texttt{-}, \texttt{charConst}, \texttt{ident}, \texttt{new}, \texttt{number} \\ \hline
\texttt{Expr\_Minus} & $\epsilon$, \texttt{-} \\ \hline
\texttt{Expr\_Opt} & $\epsilon$, \texttt{(}, \texttt{-}, \texttt{charConst}, \texttt{ident}, \texttt{new}, \texttt{number} \\ \hline
\texttt{Expr\_Tail} & $\epsilon$, \texttt{+}, \texttt{-} \\ \hline
\texttt{Factor} & \texttt{(}, \texttt{charConst}, \texttt{ident}, \texttt{new}, \texttt{number} \\ \hline
\texttt{Factor\_Designator} & $\epsilon$, \texttt{(} \\ \hline
\texttt{Factor\_New} & $\epsilon$, \texttt{[} \\ \hline
\texttt{FormPars} & \texttt{ident} \\ \hline
\texttt{FormPars\_Opt} & $\epsilon$, \texttt{ident} \\ \hline
\texttt{FormPars\_Tail} & $\epsilon$, \texttt{,} \\ \hline
\texttt{MethodDecl} & \texttt{ident}, \texttt{void} \\ \hline
\texttt{MethodDecls} & $\epsilon$, \texttt{ident}, \texttt{void} \\ \hline
\texttt{MethodType} & \texttt{ident}, \texttt{void} \\ \hline
\texttt{Mulop} & \texttt{\%}, \texttt{*}, \texttt{/} \\ \hline
\texttt{Print\_Opt} & $\epsilon$, \texttt{,} \\ \hline
\texttt{Program} & \texttt{program} \\ \hline
\texttt{Program\_Body} & $\epsilon$, \texttt{class}, \texttt{final}, \texttt{ident} \\ \hline
\texttt{Relop} & \texttt{!=}, \texttt{<}, \texttt{<=}, \texttt{==}, \texttt{>}, \texttt{>=} \\ \hline
\texttt{Statement} & \texttt{;}, \texttt{ident}, \texttt{if}, \texttt{print}, \texttt{read}, \texttt{return}, \texttt{while}, \texttt{\{} \\ \hline
\texttt{Statement\_AssignOrCall} & \texttt{(}, \texttt{=} \\ \hline
\texttt{Statements} & $\epsilon$, \texttt{;}, \texttt{ident}, \texttt{if}, \texttt{print}, \texttt{read}, \texttt{return}, \texttt{while}, \texttt{\{} \\ \hline
\texttt{Term} & \texttt{(}, \texttt{charConst}, \texttt{ident}, \texttt{new}, \texttt{number} \\ \hline
\texttt{Term\_Tail} & $\epsilon$, \texttt{\%}, \texttt{*}, \texttt{/} \\ \hline
\texttt{Type} & \texttt{ident} \\ \hline
\texttt{Type\_Opt} & $\epsilon$, \texttt{[} \\ \hline
\texttt{VarDecl} & \texttt{ident} \\ \hline
\texttt{VarDecl\_Tail} & $\epsilon$, \texttt{,} \\ \hline
\texttt{VarDecls} & $\epsilon$, \texttt{ident} \\ \hline
\end{tabular}
\end{center}

\subsection{FOLLOW Sets}
\begin{center}
\begin{tabular}{|l|p{10cm}|}
\hline
\textbf{Non-Terminal} & \textbf{FOLLOW Set} \\ \hline
\texttt{ActPars} & \texttt{!=}, \texttt{\%}, \texttt{)}, \texttt{*}, \texttt{+}, \texttt{,}, \texttt{-}, \texttt{/}, \texttt{;}, \texttt{<}, \texttt{<=}, \texttt{==}, \texttt{>}, \texttt{>=}, \texttt{]} \\ \hline
\texttt{ActPars\_List} & \texttt{)} \\ \hline
\texttt{ActPars\_Tail} & \texttt{)} \\ \hline
\texttt{Addop} & \texttt{(}, \texttt{charConst}, \texttt{ident}, \texttt{new}, \texttt{number} \\ \hline
\texttt{Block} & \texttt{;}, \texttt{else}, \texttt{ident}, \texttt{if}, \texttt{print}, \texttt{read}, \texttt{return}, \texttt{void}, \texttt{while}, \texttt{\{}, \texttt{\}} \\ \hline
\texttt{ClassDecl} & \texttt{class}, \texttt{final}, \texttt{ident}, \texttt{\{} \\ \hline
\texttt{Condition} & \texttt{)} \\ \hline
\texttt{ConstDecl} & \texttt{class}, \texttt{final}, \texttt{ident}, \texttt{\{} \\ \hline
\texttt{ConstValue} & \texttt{;} \\ \hline
\texttt{Designator} & \texttt{!=}, \texttt{\%}, \texttt{(}, \texttt{)}, \texttt{*}, \texttt{+}, \texttt{,}, \texttt{-}, \texttt{/}, \texttt{;}, \texttt{<}, \texttt{<=}, \texttt{=}, \texttt{==}, \texttt{>}, \texttt{>=}, \texttt{]} \\ \hline
\texttt{Designator\_Tail} & \texttt{!=}, \texttt{\%}, \texttt{(}, \texttt{)}, \texttt{*}, \texttt{+}, \texttt{,}, \texttt{-}, \texttt{/}, \texttt{;}, \texttt{<}, \texttt{<=}, \texttt{=}, \texttt{==}, \texttt{>}, \texttt{>=}, \texttt{]} \\ \hline
\texttt{Else\_Opt} & \texttt{;}, \texttt{else}, \texttt{ident}, \texttt{if}, \texttt{print}, \texttt{read}, \texttt{return}, \texttt{while}, \texttt{\{}, \texttt{\}} \\ \hline
\texttt{Expr} & \texttt{!=}, \texttt{)}, \texttt{,}, \texttt{;}, \texttt{<}, \texttt{<=}, \texttt{==}, \texttt{>}, \texttt{>=}, \texttt{]} \\ \hline
\texttt{Expr\_Minus} & \texttt{(}, \texttt{charConst}, \texttt{ident}, \texttt{new}, \texttt{number} \\ \hline
\texttt{Expr\_Opt} & \texttt{;} \\ \hline
\texttt{Expr\_Tail} & \texttt{!=}, \texttt{)}, \texttt{,}, \texttt{;}, \texttt{<}, \texttt{<=}, \texttt{==}, \texttt{>}, \texttt{>=}, \texttt{]} \\ \hline
\texttt{Factor} & \texttt{!=}, \texttt{\%}, \texttt{)}, \texttt{*}, \texttt{+}, \texttt{,}, \texttt{-}, \texttt{/}, \texttt{;}, \texttt{<}, \texttt{<=}, \texttt{==}, \texttt{>}, \texttt{>=}, \texttt{]} \\ \hline
\texttt{Factor\_Designator} & \texttt{!=}, \texttt{\%}, \texttt{)}, \texttt{*}, \texttt{+}, \texttt{,}, \texttt{-}, \texttt{/}, \texttt{;}, \texttt{<}, \texttt{<=}, \texttt{==}, \texttt{>}, \texttt{>=}, \texttt{]} \\ \hline
\texttt{Factor\_New} & \texttt{!=}, \texttt{\%}, \texttt{)}, \texttt{*}, \texttt{+}, \texttt{,}, \texttt{-}, \texttt{/}, \texttt{;}, \texttt{<}, \texttt{<=}, \texttt{==}, \texttt{>}, \texttt{>=}, \texttt{]} \\ \hline
\texttt{FormPars} & \texttt{)} \\ \hline
\texttt{FormPars\_Opt} & \texttt{)} \\ \hline
\texttt{FormPars\_Tail} & \texttt{)} \\ \hline
\texttt{MethodDecl} & \texttt{ident}, \texttt{void}, \texttt{\}} \\ \hline
\texttt{MethodDecls} & \texttt{\}} \\ \hline
\texttt{MethodType} & \texttt{ident} \\ \hline
\texttt{Mulop} & \texttt{(}, \texttt{charConst}, \texttt{ident}, \texttt{new}, \texttt{number} \\ \hline
\texttt{Print\_Opt} & \texttt{)} \\ \hline
\texttt{Program} & \texttt{\$} \\ \hline
\texttt{Program\_Body} & \texttt{\{} \\ \hline
\texttt{Relop} & \texttt{(}, \texttt{-}, \texttt{charConst}, \texttt{ident}, \texttt{new}, \texttt{number} \\ \hline
\texttt{Statement} & \texttt{;}, \texttt{else}, \texttt{ident}, \texttt{if}, \texttt{print}, \texttt{read}, \texttt{return}, \texttt{while}, \texttt{\{}, \texttt{\}} \\ \hline
\texttt{Statement\_AssignOrCall} & \texttt{;}, \texttt{else}, \texttt{ident}, \texttt{if}, \texttt{print}, \texttt{read}, \texttt{return}, \texttt{while}, \texttt{\{}, \texttt{\}} \\ \hline
\texttt{Statements} & \texttt{\}} \\ \hline
\texttt{Term} & \texttt{!=}, \texttt{)}, \texttt{+}, \texttt{,}, \texttt{-}, \texttt{;}, \texttt{<}, \texttt{<=}, \texttt{==}, \texttt{>}, \texttt{>=}, \texttt{]} \\ \hline
\texttt{Term\_Tail} & \texttt{!=}, \texttt{)}, \texttt{+}, \texttt{,}, \texttt{-}, \texttt{;}, \texttt{<}, \texttt{<=}, \texttt{==}, \texttt{>}, \texttt{>=}, \texttt{]} \\ \hline
\texttt{Type} & \texttt{ident} \\ \hline
\texttt{Type\_Opt} & \texttt{ident} \\ \hline
\texttt{VarDecl} & \texttt{class}, \texttt{final}, \texttt{ident}, \texttt{\{}, \texttt{\}} \\ \hline
\texttt{VarDecl\_Tail} & \texttt{;} \\ \hline
\texttt{VarDecls} & \texttt{\{}, \texttt{\}} \\ \hline
\end{tabular}
\end{center}

\subsection{LL(1) Predictive Parsing Table (Representative Subset)}
\begin{center}
\begin{tabular}{|l|l|p{8cm}|}
\hline
\textbf{Non-Terminal} & \textbf{Input Token} & \textbf{Applied Rule} \\ \hline
\texttt{ActPars} & \texttt{(} & $ActPars \rightarrow ( ActPars\_List )$ \\ \hline
\texttt{ActPars\_List} & \texttt{(} & $ActPars\_List \rightarrow Expr ActPars\_Tail$ \\ \hline
\texttt{ActPars\_List} & \texttt{)} & $ActPars\_List \rightarrow \epsilon$ \\ \hline
\texttt{ActPars\_List} & \texttt{-} & $ActPars\_List \rightarrow Expr ActPars\_Tail$ \\ \hline
\texttt{ActPars\_List} & \texttt{charConst} & $ActPars\_List \rightarrow Expr ActPars\_Tail$ \\ \hline
\texttt{ActPars\_List} & \texttt{ident} & $ActPars\_List \rightarrow Expr ActPars\_Tail$ \\ \hline
\texttt{ActPars\_List} & \texttt{new} & $ActPars\_List \rightarrow Expr ActPars\_Tail$ \\ \hline
\texttt{ActPars\_List} & \texttt{number} & $ActPars\_List \rightarrow Expr ActPars\_Tail$ \\ \hline
\texttt{ActPars\_Tail} & \texttt{)} & $ActPars\_Tail \rightarrow \epsilon$ \\ \hline
\texttt{ActPars\_Tail} & \texttt{,} & $ActPars\_Tail \rightarrow , Expr ActPars\_Tail$ \\ \hline
\texttt{Addop} & \texttt{+} & $Addop \rightarrow +$ \\ \hline
\texttt{Addop} & \texttt{-} & $Addop \rightarrow -$ \\ \hline
\texttt{Block} & \texttt{\{} & $Block \rightarrow \{ Statements \}$ \\ \hline
\texttt{ClassDecl} & \texttt{class} & $ClassDecl \rightarrow class ident \{ VarDecls \}$ \\ \hline
\texttt{Condition} & \texttt{(} & $Condition \rightarrow Expr Relop Expr$ \\ \hline
\texttt{Condition} & \texttt{-} & $Condition \rightarrow Expr Relop Expr$ \\ \hline
\texttt{Condition} & \texttt{charConst} & $Condition \rightarrow Expr Relop Expr$ \\ \hline
\texttt{Condition} & \texttt{ident} & $Condition \rightarrow Expr Relop Expr$ \\ \hline
\texttt{Condition} & \texttt{new} & $Condition \rightarrow Expr Relop Expr$ \\ \hline
\texttt{Condition} & \texttt{number} & $Condition \rightarrow Expr Relop Expr$ \\ \hline
\texttt{ConstDecl} & \texttt{final} & $ConstDecl \rightarrow final Type ident = ConstValue ;$ \\ \hline
\texttt{ConstValue} & \texttt{charConst} & $ConstValue \rightarrow charConst$ \\ \hline
\texttt{ConstValue} & \texttt{number} & $ConstValue \rightarrow number$ \\ \hline
\texttt{Designator} & \texttt{ident} & $Designator \rightarrow ident Designator\_Tail$ \\ \hline
\end{tabular}
\end{center}

\newpage

\section{Canonical LR(1) Action, GOTO, and Trace Output}
The Canonical LR(1) parser generates 381 states. Below is the representative subset of the generated Action and Goto tables for the first 30 states, followed by an execution stack trace.

\subsection{Action and Goto Tables (All 381 States)}
\begin{longtable}{|c|p{7.5cm}|p{6.5cm}|}
\hline
\textbf{State} & \textbf{Action Transitions (Terminal $\rightarrow$ Action)} & \textbf{GOTO Transitions (Non-Terminal $\rightarrow$ State)} \\ \hline
\endfirsthead
\hline
\textbf{State} & \textbf{Action Transitions (Terminal $\rightarrow$ Action)} & \textbf{GOTO Transitions (Non-Terminal $\rightarrow$ State)} \\ \hline
\endhead
\hline
\endfoot
\hline
\endlastfoot
0 & \texttt{program} $\rightarrow$ \texttt{S1} & \texttt{Program} $\rightarrow$ 2 \\ \hline
1 & \texttt{ident} $\rightarrow$ \texttt{S3} & None \\ \hline
2 & \texttt{\$} $\rightarrow$ \texttt{acc} & None \\ \hline
3 & \texttt{final} $\rightarrow$ \texttt{S9}, \texttt{class} $\rightarrow$ \texttt{S10}, \texttt{ident} $\rightarrow$ \texttt{S6}, \texttt{\{} $\rightarrow$ \texttt{R5} & \texttt{ClassDecl} $\rightarrow$ 4, \texttt{Program\_Body} $\rightarrow$ 5, \texttt{VarDecl} $\rightarrow$ 7, \texttt{Type} $\rightarrow$ 8, \texttt{ConstDecl} $\rightarrow$ 11 \\ \hline
4 & \texttt{final} $\rightarrow$ \texttt{S9}, \texttt{class} $\rightarrow$ \texttt{S10}, \texttt{ident} $\rightarrow$ \texttt{S6}, \texttt{\{} $\rightarrow$ \texttt{R5} & \texttt{ClassDecl} $\rightarrow$ 4, \texttt{Program\_Body} $\rightarrow$ 12, \texttt{VarDecl} $\rightarrow$ 7, \texttt{Type} $\rightarrow$ 8, \texttt{ConstDecl} $\rightarrow$ 11 \\ \hline
5 & \texttt{\{} $\rightarrow$ \texttt{S13} & None \\ \hline
6 & \texttt{[} $\rightarrow$ \texttt{S15}, \texttt{ident} $\rightarrow$ \texttt{R27} & \texttt{Type\_Opt} $\rightarrow$ 14 \\ \hline
7 & \texttt{final} $\rightarrow$ \texttt{S9}, \texttt{class} $\rightarrow$ \texttt{S10}, \texttt{ident} $\rightarrow$ \texttt{S6}, \texttt{\{} $\rightarrow$ \texttt{R5} & \texttt{ClassDecl} $\rightarrow$ 4, \texttt{Program\_Body} $\rightarrow$ 16, \texttt{VarDecl} $\rightarrow$ 7, \texttt{Type} $\rightarrow$ 8, \texttt{ConstDecl} $\rightarrow$ 11 \\ \hline
8 & \texttt{ident} $\rightarrow$ \texttt{S17} & None \\ \hline
9 & \texttt{ident} $\rightarrow$ \texttt{S6} & \texttt{Type} $\rightarrow$ 18 \\ \hline
10 & \texttt{ident} $\rightarrow$ \texttt{S19} & None \\ \hline
11 & \texttt{final} $\rightarrow$ \texttt{S9}, \texttt{class} $\rightarrow$ \texttt{S10}, \texttt{ident} $\rightarrow$ \texttt{S6}, \texttt{\{} $\rightarrow$ \texttt{R5} & \texttt{ClassDecl} $\rightarrow$ 4, \texttt{Program\_Body} $\rightarrow$ 20, \texttt{VarDecl} $\rightarrow$ 7, \texttt{Type} $\rightarrow$ 8, \texttt{ConstDecl} $\rightarrow$ 11 \\ \hline
12 & \texttt{\{} $\rightarrow$ \texttt{R4} & None \\ \hline
13 & \texttt{ident} $\rightarrow$ \texttt{S6}, \texttt{void} $\rightarrow$ \texttt{S21}, \texttt{\}} $\rightarrow$ \texttt{R16} & \texttt{MethodDecl} $\rightarrow$ 22, \texttt{Type} $\rightarrow$ 23, \texttt{MethodType} $\rightarrow$ 24, \texttt{MethodDecls} $\rightarrow$ 25 \\ \hline
14 & \texttt{ident} $\rightarrow$ \texttt{R25} & None \\ \hline
15 & \texttt{]} $\rightarrow$ \texttt{S26} & None \\ \hline
16 & \texttt{\{} $\rightarrow$ \texttt{R3} & None \\ \hline
17 & \texttt{,} $\rightarrow$ \texttt{S28}, \texttt{;} $\rightarrow$ \texttt{R11} & \texttt{VarDecl\_Tail} $\rightarrow$ 27 \\ \hline
18 & \texttt{ident} $\rightarrow$ \texttt{S29} & None \\ \hline
19 & \texttt{\{} $\rightarrow$ \texttt{S30} & None \\ \hline
20 & \texttt{\{} $\rightarrow$ \texttt{R2} & None \\ \hline
21 & \texttt{ident} $\rightarrow$ \texttt{R19} & None \\ \hline
22 & \texttt{ident} $\rightarrow$ \texttt{S6}, \texttt{void} $\rightarrow$ \texttt{S21}, \texttt{\}} $\rightarrow$ \texttt{R16} & \texttt{MethodDecl} $\rightarrow$ 22, \texttt{Type} $\rightarrow$ 23, \texttt{MethodType} $\rightarrow$ 24, \texttt{MethodDecls} $\rightarrow$ 31 \\ \hline
23 & \texttt{ident} $\rightarrow$ \texttt{R18} & None \\ \hline
24 & \texttt{ident} $\rightarrow$ \texttt{S32} & None \\ \hline
25 & \texttt{\}} $\rightarrow$ \texttt{S33} & None \\ \hline
26 & \texttt{ident} $\rightarrow$ \texttt{R26} & None \\ \hline
27 & \texttt{;} $\rightarrow$ \texttt{S34} & None \\ \hline
28 & \texttt{ident} $\rightarrow$ \texttt{S35} & None \\ \hline
29 & \texttt{=} $\rightarrow$ \texttt{S36} & None \\ \hline
30 & \texttt{\}} $\rightarrow$ \texttt{R14}, \texttt{ident} $\rightarrow$ \texttt{S6} & \texttt{VarDecl} $\rightarrow$ 37, \texttt{Type} $\rightarrow$ 38, \texttt{VarDecls} $\rightarrow$ 39 \\ \hline
31 & \texttt{\}} $\rightarrow$ \texttt{R15} & None \\ \hline
32 & \texttt{(} $\rightarrow$ \texttt{S40} & None \\ \hline
33 & \texttt{\$} $\rightarrow$ \texttt{R1} & None \\ \hline
34 & \texttt{\{} $\rightarrow$ \texttt{R9}, \texttt{ident} $\rightarrow$ \texttt{R9}, \texttt{final} $\rightarrow$ \texttt{R9}, \texttt{class} $\rightarrow$ \texttt{R9} & None \\ \hline
35 & \texttt{,} $\rightarrow$ \texttt{S28}, \texttt{;} $\rightarrow$ \texttt{R11} & \texttt{VarDecl\_Tail} $\rightarrow$ 41 \\ \hline
36 & \texttt{number} $\rightarrow$ \texttt{S42}, \texttt{charConst} $\rightarrow$ \texttt{S43} & \texttt{ConstValue} $\rightarrow$ 44 \\ \hline
37 & \texttt{\}} $\rightarrow$ \texttt{R14}, \texttt{ident} $\rightarrow$ \texttt{S6} & \texttt{VarDecl} $\rightarrow$ 37, \texttt{Type} $\rightarrow$ 38, \texttt{VarDecls} $\rightarrow$ 45 \\ \hline
38 & \texttt{ident} $\rightarrow$ \texttt{S46} & None \\ \hline
39 & \texttt{\}} $\rightarrow$ \texttt{S47} & None \\ \hline
40 & \texttt{)} $\rightarrow$ \texttt{R21}, \texttt{ident} $\rightarrow$ \texttt{S6} & \texttt{FormPars\_Opt} $\rightarrow$ 48, \texttt{Type} $\rightarrow$ 49, \texttt{FormPars} $\rightarrow$ 50 \\ \hline
41 & \texttt{;} $\rightarrow$ \texttt{R10} & None \\ \hline
42 & \texttt{;} $\rightarrow$ \texttt{R7} & None \\ \hline
43 & \texttt{;} $\rightarrow$ \texttt{R8} & None \\ \hline
44 & \texttt{;} $\rightarrow$ \texttt{S51} & None \\ \hline
45 & \texttt{\}} $\rightarrow$ \texttt{R13} & None \\ \hline
46 & \texttt{;} $\rightarrow$ \texttt{R11}, \texttt{,} $\rightarrow$ \texttt{S28} & \texttt{VarDecl\_Tail} $\rightarrow$ 52 \\ \hline
47 & \texttt{class} $\rightarrow$ \texttt{R12}, \texttt{\{} $\rightarrow$ \texttt{R12}, \texttt{ident} $\rightarrow$ \texttt{R12}, \texttt{final} $\rightarrow$ \texttt{R12} & None \\ \hline
48 & \texttt{)} $\rightarrow$ \texttt{S53} & None \\ \hline
49 & \texttt{ident} $\rightarrow$ \texttt{S54} & None \\ \hline
50 & \texttt{)} $\rightarrow$ \texttt{R20} & None \\ \hline
51 & \texttt{class} $\rightarrow$ \texttt{R6}, \texttt{\{} $\rightarrow$ \texttt{R6}, \texttt{ident} $\rightarrow$ \texttt{R6}, \texttt{final} $\rightarrow$ \texttt{R6} & None \\ \hline
52 & \texttt{;} $\rightarrow$ \texttt{S55} & None \\ \hline
53 & \texttt{ident} $\rightarrow$ \texttt{S6}, \texttt{\{} $\rightarrow$ \texttt{R14} & \texttt{VarDecl} $\rightarrow$ 56, \texttt{Type} $\rightarrow$ 57, \texttt{VarDecls} $\rightarrow$ 58 \\ \hline
54 & \texttt{)} $\rightarrow$ \texttt{R24}, \texttt{,} $\rightarrow$ \texttt{S59} & \texttt{FormPars\_Tail} $\rightarrow$ 60 \\ \hline
55 & \texttt{ident} $\rightarrow$ \texttt{R9}, \texttt{\}} $\rightarrow$ \texttt{R9} & None \\ \hline
56 & \texttt{\{} $\rightarrow$ \texttt{R14}, \texttt{ident} $\rightarrow$ \texttt{S6} & \texttt{VarDecl} $\rightarrow$ 56, \texttt{Type} $\rightarrow$ 57, \texttt{VarDecls} $\rightarrow$ 61 \\ \hline
57 & \texttt{ident} $\rightarrow$ \texttt{S62} & None \\ \hline
58 & \texttt{\{} $\rightarrow$ \texttt{S64} & \texttt{Block} $\rightarrow$ 63 \\ \hline
59 & \texttt{ident} $\rightarrow$ \texttt{S6} & \texttt{Type} $\rightarrow$ 65 \\ \hline
60 & \texttt{)} $\rightarrow$ \texttt{R22} & None \\ \hline
61 & \texttt{\{} $\rightarrow$ \texttt{R13} & None \\ \hline
62 & \texttt{,} $\rightarrow$ \texttt{S28}, \texttt{;} $\rightarrow$ \texttt{R11} & \texttt{VarDecl\_Tail} $\rightarrow$ 66 \\ \hline
63 & \texttt{ident} $\rightarrow$ \texttt{R17}, \texttt{\}} $\rightarrow$ \texttt{R17}, \texttt{void} $\rightarrow$ \texttt{R17} & None \\ \hline
64 & \texttt{read} $\rightarrow$ \texttt{S76}, \texttt{print} $\rightarrow$ \texttt{S77}, \texttt{if} $\rightarrow$ \texttt{S78}, \texttt{while} $\rightarrow$ \texttt{S74}, \texttt{\{} $\rightarrow$ \texttt{S68}, \texttt{;} $\rightarrow$ \texttt{S67}, \texttt{return} $\rightarrow$ \texttt{S70}, \texttt{\}} $\rightarrow$ \texttt{R30}, \texttt{ident} $\rightarrow$ \texttt{S73} & \texttt{Designator} $\rightarrow$ 69, \texttt{Statements} $\rightarrow$ 71, \texttt{Statement} $\rightarrow$ 72, \texttt{Block} $\rightarrow$ 75 \\ \hline
65 & \texttt{ident} $\rightarrow$ \texttt{S79} & None \\ \hline
66 & \texttt{;} $\rightarrow$ \texttt{S80} & None \\ \hline
67 & \texttt{read} $\rightarrow$ \texttt{R38}, \texttt{\}} $\rightarrow$ \texttt{R38}, \texttt{\{} $\rightarrow$ \texttt{R38}, \texttt{ident} $\rightarrow$ \texttt{R38}, \texttt{while} $\rightarrow$ \texttt{R38}, \texttt{;} $\rightarrow$ \texttt{R38}, \texttt{return} $\rightarrow$ \texttt{R38}, \texttt{if} $\rightarrow$ \texttt{R38}, \texttt{print} $\rightarrow$ \texttt{R38} & None \\ \hline
68 & \texttt{read} $\rightarrow$ \texttt{S76}, \texttt{print} $\rightarrow$ \texttt{S77}, \texttt{if} $\rightarrow$ \texttt{S78}, \texttt{while} $\rightarrow$ \texttt{S74}, \texttt{\{} $\rightarrow$ \texttt{S68}, \texttt{;} $\rightarrow$ \texttt{S67}, \texttt{return} $\rightarrow$ \texttt{S70}, \texttt{\}} $\rightarrow$ \texttt{R30}, \texttt{ident} $\rightarrow$ \texttt{S73} & \texttt{Designator} $\rightarrow$ 69, \texttt{Statements} $\rightarrow$ 81, \texttt{Statement} $\rightarrow$ 72, \texttt{Block} $\rightarrow$ 75 \\ \hline
69 & \texttt{=} $\rightarrow$ \texttt{S84}, \texttt{(} $\rightarrow$ \texttt{S83} & \texttt{Statement\_AssignOrCall} $\rightarrow$ 82, \texttt{ActPars} $\rightarrow$ 85 \\ \hline
70 & \texttt{-} $\rightarrow$ \texttt{S88}, \texttt{charConst} $\rightarrow$ \texttt{R61}, \texttt{;} $\rightarrow$ \texttt{R44}, \texttt{(} $\rightarrow$ \texttt{R61}, \texttt{new} $\rightarrow$ \texttt{R61}, \texttt{number} $\rightarrow$ \texttt{R61}, \texttt{ident} $\rightarrow$ \texttt{R61} & \texttt{Expr\_Minus} $\rightarrow$ 86, \texttt{Expr} $\rightarrow$ 87, \texttt{Expr\_Opt} $\rightarrow$ 89 \\ \hline
71 & \texttt{\}} $\rightarrow$ \texttt{S90} & None \\ \hline
72 & \texttt{read} $\rightarrow$ \texttt{S76}, \texttt{print} $\rightarrow$ \texttt{S77}, \texttt{if} $\rightarrow$ \texttt{S78}, \texttt{while} $\rightarrow$ \texttt{S74}, \texttt{\{} $\rightarrow$ \texttt{S68}, \texttt{;} $\rightarrow$ \texttt{S67}, \texttt{return} $\rightarrow$ \texttt{S70}, \texttt{\}} $\rightarrow$ \texttt{R30}, \texttt{ident} $\rightarrow$ \texttt{S73} & \texttt{Designator} $\rightarrow$ 69, \texttt{Statements} $\rightarrow$ 91, \texttt{Statement} $\rightarrow$ 72, \texttt{Block} $\rightarrow$ 75 \\ \hline
73 & \texttt{(} $\rightarrow$ \texttt{R84}, \texttt{=} $\rightarrow$ \texttt{R84}, \texttt{[} $\rightarrow$ \texttt{S92}, \texttt{.} $\rightarrow$ \texttt{S94} & \texttt{Designator\_Tail} $\rightarrow$ 93 \\ \hline
74 & \texttt{(} $\rightarrow$ \texttt{S95} & None \\ \hline
75 & \texttt{\{} $\rightarrow$ \texttt{R37}, \texttt{;} $\rightarrow$ \texttt{R37}, \texttt{while} $\rightarrow$ \texttt{R37}, \texttt{ident} $\rightarrow$ \texttt{R37}, \texttt{print} $\rightarrow$ \texttt{R37}, \texttt{return} $\rightarrow$ \texttt{R37}, \texttt{\}} $\rightarrow$ \texttt{R37}, \texttt{if} $\rightarrow$ \texttt{R37}, \texttt{read} $\rightarrow$ \texttt{R37} & None \\ \hline
76 & \texttt{(} $\rightarrow$ \texttt{S96} & None \\ \hline
77 & \texttt{(} $\rightarrow$ \texttt{S97} & None \\ \hline
78 & \texttt{(} $\rightarrow$ \texttt{S98} & None \\ \hline
79 & \texttt{)} $\rightarrow$ \texttt{R24}, \texttt{,} $\rightarrow$ \texttt{S59} & \texttt{FormPars\_Tail} $\rightarrow$ 99 \\ \hline
80 & \texttt{\{} $\rightarrow$ \texttt{R9}, \texttt{ident} $\rightarrow$ \texttt{R9} & None \\ \hline
81 & \texttt{\}} $\rightarrow$ \texttt{S100} & None \\ \hline
82 & \texttt{;} $\rightarrow$ \texttt{R31}, \texttt{while} $\rightarrow$ \texttt{R31}, \texttt{ident} $\rightarrow$ \texttt{R31}, \texttt{return} $\rightarrow$ \texttt{R31}, \texttt{if} $\rightarrow$ \texttt{R31}, \texttt{\}} $\rightarrow$ \texttt{R31}, \texttt{print} $\rightarrow$ \texttt{R31}, \texttt{read} $\rightarrow$ \texttt{R31}, \texttt{\{} $\rightarrow$ \texttt{R31} & None \\ \hline
83 & \texttt{-} $\rightarrow$ \texttt{S88}, \texttt{number} $\rightarrow$ \texttt{R61}, \texttt{charConst} $\rightarrow$ \texttt{R61}, \texttt{ident} $\rightarrow$ \texttt{R61}, \texttt{(} $\rightarrow$ \texttt{R61}, \texttt{new} $\rightarrow$ \texttt{R61}, \texttt{)} $\rightarrow$ \texttt{R49} & \texttt{Expr\_Minus} $\rightarrow$ 101, \texttt{ActPars\_List} $\rightarrow$ 102, \texttt{Expr} $\rightarrow$ 103 \\ \hline
84 & \texttt{-} $\rightarrow$ \texttt{S88}, \texttt{charConst} $\rightarrow$ \texttt{R61}, \texttt{(} $\rightarrow$ \texttt{R61}, \texttt{new} $\rightarrow$ \texttt{R61}, \texttt{number} $\rightarrow$ \texttt{R61}, \texttt{ident} $\rightarrow$ \texttt{R61} & \texttt{Expr\_Minus} $\rightarrow$ 86, \texttt{Expr} $\rightarrow$ 104 \\ \hline
85 & \texttt{;} $\rightarrow$ \texttt{S105} & None \\ \hline
86 & \texttt{(} $\rightarrow$ \texttt{S108}, \texttt{new} $\rightarrow$ \texttt{S113}, \texttt{charConst} $\rightarrow$ \texttt{S109}, \texttt{ident} $\rightarrow$ \texttt{S111}, \texttt{number} $\rightarrow$ \texttt{S107} & \texttt{Term} $\rightarrow$ 106, \texttt{Factor} $\rightarrow$ 110, \texttt{Designator} $\rightarrow$ 112 \\ \hline
87 & \texttt{;} $\rightarrow$ \texttt{R43} & None \\ \hline
88 & \texttt{number} $\rightarrow$ \texttt{R60}, \texttt{charConst} $\rightarrow$ \texttt{R60}, \texttt{(} $\rightarrow$ \texttt{R60}, \texttt{ident} $\rightarrow$ \texttt{R60}, \texttt{new} $\rightarrow$ \texttt{R60} & None \\ \hline
89 & \texttt{;} $\rightarrow$ \texttt{S114} & None \\ \hline
90 & \texttt{\}} $\rightarrow$ \texttt{R28}, \texttt{ident} $\rightarrow$ \texttt{R28}, \texttt{void} $\rightarrow$ \texttt{R28} & None \\ \hline
91 & \texttt{\}} $\rightarrow$ \texttt{R29} & None \\ \hline
92 & \texttt{-} $\rightarrow$ \texttt{S88}, \texttt{number} $\rightarrow$ \texttt{R61}, \texttt{charConst} $\rightarrow$ \texttt{R61}, \texttt{ident} $\rightarrow$ \texttt{R61}, \texttt{(} $\rightarrow$ \texttt{R61}, \texttt{new} $\rightarrow$ \texttt{R61} & \texttt{Expr\_Minus} $\rightarrow$ 115, \texttt{Expr} $\rightarrow$ 116 \\ \hline
93 & \texttt{=} $\rightarrow$ \texttt{R81}, \texttt{(} $\rightarrow$ \texttt{R81} & None \\ \hline
94 & \texttt{ident} $\rightarrow$ \texttt{S117} & None \\ \hline
95 & \texttt{-} $\rightarrow$ \texttt{S88}, \texttt{charConst} $\rightarrow$ \texttt{R61}, \texttt{(} $\rightarrow$ \texttt{R61}, \texttt{new} $\rightarrow$ \texttt{R61}, \texttt{number} $\rightarrow$ \texttt{R61}, \texttt{ident} $\rightarrow$ \texttt{R61} & \texttt{Expr\_Minus} $\rightarrow$ 118, \texttt{Condition} $\rightarrow$ 119, \texttt{Expr} $\rightarrow$ 120 \\ \hline
96 & \texttt{ident} $\rightarrow$ \texttt{S122} & \texttt{Designator} $\rightarrow$ 121 \\ \hline
97 & \texttt{-} $\rightarrow$ \texttt{S88}, \texttt{charConst} $\rightarrow$ \texttt{R61}, \texttt{(} $\rightarrow$ \texttt{R61}, \texttt{new} $\rightarrow$ \texttt{R61}, \texttt{number} $\rightarrow$ \texttt{R61}, \texttt{ident} $\rightarrow$ \texttt{R61} & \texttt{Expr\_Minus} $\rightarrow$ 101, \texttt{Expr} $\rightarrow$ 123 \\ \hline
98 & \texttt{-} $\rightarrow$ \texttt{S88}, \texttt{charConst} $\rightarrow$ \texttt{R61}, \texttt{(} $\rightarrow$ \texttt{R61}, \texttt{new} $\rightarrow$ \texttt{R61}, \texttt{number} $\rightarrow$ \texttt{R61}, \texttt{ident} $\rightarrow$ \texttt{R61} & \texttt{Expr\_Minus} $\rightarrow$ 118, \texttt{Condition} $\rightarrow$ 124, \texttt{Expr} $\rightarrow$ 120 \\ \hline
99 & \texttt{)} $\rightarrow$ \texttt{R23} & None \\ \hline
100 & \texttt{\{} $\rightarrow$ \texttt{R28}, \texttt{;} $\rightarrow$ \texttt{R28}, \texttt{ident} $\rightarrow$ \texttt{R28}, \texttt{while} $\rightarrow$ \texttt{R28}, \texttt{print} $\rightarrow$ \texttt{R28}, \texttt{return} $\rightarrow$ \texttt{R28}, \texttt{if} $\rightarrow$ \texttt{R28}, \texttt{\}} $\rightarrow$ \texttt{R28}, \texttt{read} $\rightarrow$ \texttt{R28} & None \\ \hline
101 & \texttt{(} $\rightarrow$ \texttt{S127}, \texttt{new} $\rightarrow$ \texttt{S132}, \texttt{charConst} $\rightarrow$ \texttt{S128}, \texttt{number} $\rightarrow$ \texttt{S125}, \texttt{ident} $\rightarrow$ \texttt{S130} & \texttt{Term} $\rightarrow$ 126, \texttt{Factor} $\rightarrow$ 129, \texttt{Designator} $\rightarrow$ 131 \\ \hline
102 & \texttt{)} $\rightarrow$ \texttt{S133} & None \\ \hline
103 & \texttt{)} $\rightarrow$ \texttt{R51}, \texttt{,} $\rightarrow$ \texttt{S134} & \texttt{ActPars\_Tail} $\rightarrow$ 135 \\ \hline
104 & \texttt{;} $\rightarrow$ \texttt{S136} & None \\ \hline
105 & \texttt{if} $\rightarrow$ \texttt{R40}, \texttt{print} $\rightarrow$ \texttt{R40}, \texttt{\}} $\rightarrow$ \texttt{R40}, \texttt{read} $\rightarrow$ \texttt{R40}, \texttt{\{} $\rightarrow$ \texttt{R40}, \texttt{ident} $\rightarrow$ \texttt{R40}, \texttt{while} $\rightarrow$ \texttt{R40}, \texttt{;} $\rightarrow$ \texttt{R40}, \texttt{return} $\rightarrow$ \texttt{R40} & None \\ \hline
106 & \texttt{-} $\rightarrow$ \texttt{S138}, \texttt{+} $\rightarrow$ \texttt{S137}, \texttt{;} $\rightarrow$ \texttt{R63} & \texttt{Addop} $\rightarrow$ 139, \texttt{Expr\_Tail} $\rightarrow$ 140 \\ \hline
107 & \texttt{;} $\rightarrow$ \texttt{R73}, \texttt{*} $\rightarrow$ \texttt{R73}, \texttt{+} $\rightarrow$ \texttt{R73}, \texttt{/} $\rightarrow$ \texttt{R73}, \texttt{-} $\rightarrow$ \texttt{R73}, \texttt{\%} $\rightarrow$ \texttt{R73} & None \\ \hline
108 & \texttt{-} $\rightarrow$ \texttt{S88}, \texttt{charConst} $\rightarrow$ \texttt{R61}, \texttt{(} $\rightarrow$ \texttt{R61}, \texttt{new} $\rightarrow$ \texttt{R61}, \texttt{number} $\rightarrow$ \texttt{R61}, \texttt{ident} $\rightarrow$ \texttt{R61} & \texttt{Expr\_Minus} $\rightarrow$ 141, \texttt{Expr} $\rightarrow$ 142 \\ \hline
109 & \texttt{*} $\rightarrow$ \texttt{R74}, \texttt{+} $\rightarrow$ \texttt{R74}, \texttt{\%} $\rightarrow$ \texttt{R74}, \texttt{-} $\rightarrow$ \texttt{R74}, \texttt{;} $\rightarrow$ \texttt{R74}, \texttt{/} $\rightarrow$ \texttt{R74} & None \\ \hline
110 & \texttt{*} $\rightarrow$ \texttt{S143}, \texttt{/} $\rightarrow$ \texttt{S144}, \texttt{\%} $\rightarrow$ \texttt{S145}, \texttt{;} $\rightarrow$ \texttt{R68}, \texttt{+} $\rightarrow$ \texttt{R68}, \texttt{-} $\rightarrow$ \texttt{R68} & \texttt{Term\_Tail} $\rightarrow$ 146, \texttt{Mulop} $\rightarrow$ 147 \\ \hline
111 & \texttt{[} $\rightarrow$ \texttt{S148}, \texttt{.} $\rightarrow$ \texttt{S150}, \texttt{*} $\rightarrow$ \texttt{R84}, \texttt{;} $\rightarrow$ \texttt{R84}, \texttt{(} $\rightarrow$ \texttt{R84}, \texttt{-} $\rightarrow$ \texttt{R84}, \texttt{+} $\rightarrow$ \texttt{R84}, \texttt{/} $\rightarrow$ \texttt{R84}, \texttt{\%} $\rightarrow$ \texttt{R84} & \texttt{Designator\_Tail} $\rightarrow$ 149 \\ \hline
112 & \texttt{*} $\rightarrow$ \texttt{R78}, \texttt{(} $\rightarrow$ \texttt{S152}, \texttt{;} $\rightarrow$ \texttt{R78}, \texttt{+} $\rightarrow$ \texttt{R78}, \texttt{/} $\rightarrow$ \texttt{R78}, \texttt{\%} $\rightarrow$ \texttt{R78}, \texttt{-} $\rightarrow$ \texttt{R78} & \texttt{Factor\_Designator} $\rightarrow$ 151, \texttt{ActPars} $\rightarrow$ 153 \\ \hline
113 & \texttt{ident} $\rightarrow$ \texttt{S154} & None \\ \hline
114 & \texttt{print} $\rightarrow$ \texttt{R34}, \texttt{return} $\rightarrow$ \texttt{R34}, \texttt{\}} $\rightarrow$ \texttt{R34}, \texttt{if} $\rightarrow$ \texttt{R34}, \texttt{read} $\rightarrow$ \texttt{R34}, \texttt{ident} $\rightarrow$ \texttt{R34}, \texttt{\{} $\rightarrow$ \texttt{R34}, \texttt{;} $\rightarrow$ \texttt{R34}, \texttt{while} $\rightarrow$ \texttt{R34} & None \\ \hline
115 & \texttt{(} $\rightarrow$ \texttt{S157}, \texttt{new} $\rightarrow$ \texttt{S162}, \texttt{charConst} $\rightarrow$ \texttt{S158}, \texttt{ident} $\rightarrow$ \texttt{S160}, \texttt{number} $\rightarrow$ \texttt{S155} & \texttt{Term} $\rightarrow$ 156, \texttt{Factor} $\rightarrow$ 159, \texttt{Designator} $\rightarrow$ 161 \\ \hline
116 & \texttt{]} $\rightarrow$ \texttt{S163} & None \\ \hline
117 & \texttt{(} $\rightarrow$ \texttt{R84}, \texttt{=} $\rightarrow$ \texttt{R84}, \texttt{[} $\rightarrow$ \texttt{S92}, \texttt{.} $\rightarrow$ \texttt{S94} & \texttt{Designator\_Tail} $\rightarrow$ 164 \\ \hline
118 & \texttt{new} $\rightarrow$ \texttt{S172}, \texttt{ident} $\rightarrow$ \texttt{S170}, \texttt{(} $\rightarrow$ \texttt{S167}, \texttt{charConst} $\rightarrow$ \texttt{S168}, \texttt{number} $\rightarrow$ \texttt{S165} & \texttt{Term} $\rightarrow$ 166, \texttt{Factor} $\rightarrow$ 169, \texttt{Designator} $\rightarrow$ 171 \\ \hline
119 & \texttt{)} $\rightarrow$ \texttt{S173} & None \\ \hline
120 & \texttt{==} $\rightarrow$ \texttt{S176}, \texttt{!=} $\rightarrow$ \texttt{S177}, \texttt{>} $\rightarrow$ \texttt{S178}, \texttt{>=} $\rightarrow$ \texttt{S179}, \texttt{<} $\rightarrow$ \texttt{S180}, \texttt{<=} $\rightarrow$ \texttt{S174} & \texttt{Relop} $\rightarrow$ 175 \\ \hline
121 & \texttt{)} $\rightarrow$ \texttt{S181} & None \\ \hline
122 & \texttt{.} $\rightarrow$ \texttt{S182}, \texttt{)} $\rightarrow$ \texttt{R84}, \texttt{[} $\rightarrow$ \texttt{S183} & \texttt{Designator\_Tail} $\rightarrow$ 184 \\ \hline
123 & \texttt{,} $\rightarrow$ \texttt{S185}, \texttt{)} $\rightarrow$ \texttt{R46} & \texttt{Print\_Opt} $\rightarrow$ 186 \\ \hline
124 & \texttt{)} $\rightarrow$ \texttt{S187} & None \\ \hline
125 & \texttt{)} $\rightarrow$ \texttt{R73}, \texttt{*} $\rightarrow$ \texttt{R73}, \texttt{+} $\rightarrow$ \texttt{R73}, \texttt{/} $\rightarrow$ \texttt{R73}, \texttt{-} $\rightarrow$ \texttt{R73}, \texttt{,} $\rightarrow$ \texttt{R73}, \texttt{\%} $\rightarrow$ \texttt{R73} & None \\ \hline
126 & \texttt{-} $\rightarrow$ \texttt{S138}, \texttt{)} $\rightarrow$ \texttt{R63}, \texttt{+} $\rightarrow$ \texttt{S137}, \texttt{,} $\rightarrow$ \texttt{R63} & \texttt{Addop} $\rightarrow$ 188, \texttt{Expr\_Tail} $\rightarrow$ 189 \\ \hline
127 & \texttt{-} $\rightarrow$ \texttt{S88}, \texttt{charConst} $\rightarrow$ \texttt{R61}, \texttt{(} $\rightarrow$ \texttt{R61}, \texttt{new} $\rightarrow$ \texttt{R61}, \texttt{number} $\rightarrow$ \texttt{R61}, \texttt{ident} $\rightarrow$ \texttt{R61} & \texttt{Expr\_Minus} $\rightarrow$ 141, \texttt{Expr} $\rightarrow$ 190 \\ \hline
128 & \texttt{*} $\rightarrow$ \texttt{R74}, \texttt{+} $\rightarrow$ \texttt{R74}, \texttt{\%} $\rightarrow$ \texttt{R74}, \texttt{-} $\rightarrow$ \texttt{R74}, \texttt{)} $\rightarrow$ \texttt{R74}, \texttt{/} $\rightarrow$ \texttt{R74}, \texttt{,} $\rightarrow$ \texttt{R74} & None \\ \hline
129 & \texttt{*} $\rightarrow$ \texttt{S143}, \texttt{/} $\rightarrow$ \texttt{S144}, \texttt{\%} $\rightarrow$ \texttt{S145}, \texttt{,} $\rightarrow$ \texttt{R68}, \texttt{+} $\rightarrow$ \texttt{R68}, \texttt{-} $\rightarrow$ \texttt{R68}, \texttt{)} $\rightarrow$ \texttt{R68} & \texttt{Term\_Tail} $\rightarrow$ 191, \texttt{Mulop} $\rightarrow$ 192 \\ \hline
130 & \texttt{)} $\rightarrow$ \texttt{R84}, \texttt{[} $\rightarrow$ \texttt{S194}, \texttt{*} $\rightarrow$ \texttt{R84}, \texttt{.} $\rightarrow$ \texttt{S193}, \texttt{(} $\rightarrow$ \texttt{R84}, \texttt{-} $\rightarrow$ \texttt{R84}, \texttt{,} $\rightarrow$ \texttt{R84}, \texttt{+} $\rightarrow$ \texttt{R84}, \texttt{/} $\rightarrow$ \texttt{R84}, \texttt{\%} $\rightarrow$ \texttt{R84} & \texttt{Designator\_Tail} $\rightarrow$ 195 \\ \hline
131 & \texttt{*} $\rightarrow$ \texttt{R78}, \texttt{(} $\rightarrow$ \texttt{S197}, \texttt{+} $\rightarrow$ \texttt{R78}, \texttt{/} $\rightarrow$ \texttt{R78}, \texttt{\%} $\rightarrow$ \texttt{R78}, \texttt{,} $\rightarrow$ \texttt{R78}, \texttt{-} $\rightarrow$ \texttt{R78}, \texttt{)} $\rightarrow$ \texttt{R78} & \texttt{Factor\_Designator} $\rightarrow$ 196, \texttt{ActPars} $\rightarrow$ 198 \\ \hline
132 & \texttt{ident} $\rightarrow$ \texttt{S199} & None \\ \hline
133 & \texttt{;} $\rightarrow$ \texttt{R47} & None \\ \hline
134 & \texttt{-} $\rightarrow$ \texttt{S88}, \texttt{number} $\rightarrow$ \texttt{R61}, \texttt{charConst} $\rightarrow$ \texttt{R61}, \texttt{ident} $\rightarrow$ \texttt{R61}, \texttt{(} $\rightarrow$ \texttt{R61}, \texttt{new} $\rightarrow$ \texttt{R61} & \texttt{Expr\_Minus} $\rightarrow$ 101, \texttt{Expr} $\rightarrow$ 200 \\ \hline
135 & \texttt{)} $\rightarrow$ \texttt{R48} & None \\ \hline
136 & \texttt{if} $\rightarrow$ \texttt{R39}, \texttt{print} $\rightarrow$ \texttt{R39}, \texttt{read} $\rightarrow$ \texttt{R39}, \texttt{\{} $\rightarrow$ \texttt{R39}, \texttt{ident} $\rightarrow$ \texttt{R39}, \texttt{while} $\rightarrow$ \texttt{R39}, \texttt{;} $\rightarrow$ \texttt{R39}, \texttt{\}} $\rightarrow$ \texttt{R39}, \texttt{return} $\rightarrow$ \texttt{R39} & None \\ \hline
137 & \texttt{number} $\rightarrow$ \texttt{R64}, \texttt{new} $\rightarrow$ \texttt{R64}, \texttt{ident} $\rightarrow$ \texttt{R64}, \texttt{(} $\rightarrow$ \texttt{R64}, \texttt{charConst} $\rightarrow$ \texttt{R64} & None \\ \hline
138 & \texttt{number} $\rightarrow$ \texttt{R65}, \texttt{ident} $\rightarrow$ \texttt{R65}, \texttt{new} $\rightarrow$ \texttt{R65}, \texttt{(} $\rightarrow$ \texttt{R65}, \texttt{charConst} $\rightarrow$ \texttt{R65} & None \\ \hline
139 & \texttt{(} $\rightarrow$ \texttt{S108}, \texttt{new} $\rightarrow$ \texttt{S113}, \texttt{charConst} $\rightarrow$ \texttt{S109}, \texttt{ident} $\rightarrow$ \texttt{S111}, \texttt{number} $\rightarrow$ \texttt{S107} & \texttt{Term} $\rightarrow$ 201, \texttt{Factor} $\rightarrow$ 110, \texttt{Designator} $\rightarrow$ 112 \\ \hline
140 & \texttt{;} $\rightarrow$ \texttt{R59} & None \\ \hline
141 & \texttt{(} $\rightarrow$ \texttt{S204}, \texttt{new} $\rightarrow$ \texttt{S209}, \texttt{charConst} $\rightarrow$ \texttt{S205}, \texttt{ident} $\rightarrow$ \texttt{S207}, \texttt{number} $\rightarrow$ \texttt{S202} & \texttt{Term} $\rightarrow$ 203, \texttt{Factor} $\rightarrow$ 206, \texttt{Designator} $\rightarrow$ 208 \\ \hline
142 & \texttt{)} $\rightarrow$ \texttt{S210} & None \\ \hline
143 & \texttt{ident} $\rightarrow$ \texttt{R69}, \texttt{(} $\rightarrow$ \texttt{R69}, \texttt{charConst} $\rightarrow$ \texttt{R69}, \texttt{number} $\rightarrow$ \texttt{R69}, \texttt{new} $\rightarrow$ \texttt{R69} & None \\ \hline
144 & \texttt{new} $\rightarrow$ \texttt{R70}, \texttt{(} $\rightarrow$ \texttt{R70}, \texttt{ident} $\rightarrow$ \texttt{R70}, \texttt{charConst} $\rightarrow$ \texttt{R70}, \texttt{number} $\rightarrow$ \texttt{R70} & None \\ \hline
145 & \texttt{ident} $\rightarrow$ \texttt{R71}, \texttt{(} $\rightarrow$ \texttt{R71}, \texttt{new} $\rightarrow$ \texttt{R71}, \texttt{number} $\rightarrow$ \texttt{R71}, \texttt{charConst} $\rightarrow$ \texttt{R71} & None \\ \hline
146 & \texttt{+} $\rightarrow$ \texttt{R66}, \texttt{-} $\rightarrow$ \texttt{R66}, \texttt{;} $\rightarrow$ \texttt{R66} & None \\ \hline
147 & \texttt{(} $\rightarrow$ \texttt{S108}, \texttt{new} $\rightarrow$ \texttt{S113}, \texttt{charConst} $\rightarrow$ \texttt{S109}, \texttt{ident} $\rightarrow$ \texttt{S111}, \texttt{number} $\rightarrow$ \texttt{S107} & \texttt{Factor} $\rightarrow$ 211, \texttt{Designator} $\rightarrow$ 112 \\ \hline
148 & \texttt{-} $\rightarrow$ \texttt{S88}, \texttt{charConst} $\rightarrow$ \texttt{R61}, \texttt{(} $\rightarrow$ \texttt{R61}, \texttt{new} $\rightarrow$ \texttt{R61}, \texttt{number} $\rightarrow$ \texttt{R61}, \texttt{ident} $\rightarrow$ \texttt{R61} & \texttt{Expr\_Minus} $\rightarrow$ 115, \texttt{Expr} $\rightarrow$ 212 \\ \hline
149 & \texttt{-} $\rightarrow$ \texttt{R81}, \texttt{(} $\rightarrow$ \texttt{R81}, \texttt{\%} $\rightarrow$ \texttt{R81}, \texttt{;} $\rightarrow$ \texttt{R81}, \texttt{*} $\rightarrow$ \texttt{R81}, \texttt{+} $\rightarrow$ \texttt{R81}, \texttt{/} $\rightarrow$ \texttt{R81} & None \\ \hline
150 & \texttt{ident} $\rightarrow$ \texttt{S213} & None \\ \hline
151 & \texttt{;} $\rightarrow$ \texttt{R72}, \texttt{*} $\rightarrow$ \texttt{R72}, \texttt{+} $\rightarrow$ \texttt{R72}, \texttt{/} $\rightarrow$ \texttt{R72}, \texttt{\%} $\rightarrow$ \texttt{R72}, \texttt{-} $\rightarrow$ \texttt{R72} & None \\ \hline
152 & \texttt{-} $\rightarrow$ \texttt{S88}, \texttt{charConst} $\rightarrow$ \texttt{R61}, \texttt{(} $\rightarrow$ \texttt{R61}, \texttt{new} $\rightarrow$ \texttt{R61}, \texttt{)} $\rightarrow$ \texttt{R49}, \texttt{number} $\rightarrow$ \texttt{R61}, \texttt{ident} $\rightarrow$ \texttt{R61} & \texttt{Expr\_Minus} $\rightarrow$ 101, \texttt{ActPars\_List} $\rightarrow$ 214, \texttt{Expr} $\rightarrow$ 103 \\ \hline
153 & \texttt{-} $\rightarrow$ \texttt{R77}, \texttt{;} $\rightarrow$ \texttt{R77}, \texttt{*} $\rightarrow$ \texttt{R77}, \texttt{+} $\rightarrow$ \texttt{R77}, \texttt{/} $\rightarrow$ \texttt{R77}, \texttt{\%} $\rightarrow$ \texttt{R77} & None \\ \hline
154 & \texttt{[} $\rightarrow$ \texttt{S215}, \texttt{*} $\rightarrow$ \texttt{R80}, \texttt{;} $\rightarrow$ \texttt{R80}, \texttt{+} $\rightarrow$ \texttt{R80}, \texttt{/} $\rightarrow$ \texttt{R80}, \texttt{\%} $\rightarrow$ \texttt{R80}, \texttt{-} $\rightarrow$ \texttt{R80} & \texttt{Factor\_New} $\rightarrow$ 216 \\ \hline
155 & \texttt{*} $\rightarrow$ \texttt{R73}, \texttt{+} $\rightarrow$ \texttt{R73}, \texttt{/} $\rightarrow$ \texttt{R73}, \texttt{-} $\rightarrow$ \texttt{R73}, \texttt{]} $\rightarrow$ \texttt{R73}, \texttt{\%} $\rightarrow$ \texttt{R73} & None \\ \hline
156 & \texttt{-} $\rightarrow$ \texttt{S138}, \texttt{+} $\rightarrow$ \texttt{S137}, \texttt{]} $\rightarrow$ \texttt{R63} & \texttt{Addop} $\rightarrow$ 217, \texttt{Expr\_Tail} $\rightarrow$ 218 \\ \hline
157 & \texttt{-} $\rightarrow$ \texttt{S88}, \texttt{charConst} $\rightarrow$ \texttt{R61}, \texttt{(} $\rightarrow$ \texttt{R61}, \texttt{new} $\rightarrow$ \texttt{R61}, \texttt{number} $\rightarrow$ \texttt{R61}, \texttt{ident} $\rightarrow$ \texttt{R61} & \texttt{Expr\_Minus} $\rightarrow$ 141, \texttt{Expr} $\rightarrow$ 219 \\ \hline
158 & \texttt{*} $\rightarrow$ \texttt{R74}, \texttt{+} $\rightarrow$ \texttt{R74}, \texttt{]} $\rightarrow$ \texttt{R74}, \texttt{\%} $\rightarrow$ \texttt{R74}, \texttt{-} $\rightarrow$ \texttt{R74}, \texttt{/} $\rightarrow$ \texttt{R74} & None \\ \hline
159 & \texttt{*} $\rightarrow$ \texttt{S143}, \texttt{/} $\rightarrow$ \texttt{S144}, \texttt{\%} $\rightarrow$ \texttt{S145}, \texttt{]} $\rightarrow$ \texttt{R68}, \texttt{+} $\rightarrow$ \texttt{R68}, \texttt{-} $\rightarrow$ \texttt{R68} & \texttt{Term\_Tail} $\rightarrow$ 220, \texttt{Mulop} $\rightarrow$ 221 \\ \hline
160 & \texttt{[} $\rightarrow$ \texttt{S222}, \texttt{.} $\rightarrow$ \texttt{S224}, \texttt{*} $\rightarrow$ \texttt{R84}, \texttt{(} $\rightarrow$ \texttt{R84}, \texttt{-} $\rightarrow$ \texttt{R84}, \texttt{]} $\rightarrow$ \texttt{R84}, \texttt{+} $\rightarrow$ \texttt{R84}, \texttt{/} $\rightarrow$ \texttt{R84}, \texttt{\%} $\rightarrow$ \texttt{R84} & \texttt{Designator\_Tail} $\rightarrow$ 223 \\ \hline
161 & \texttt{*} $\rightarrow$ \texttt{R78}, \texttt{(} $\rightarrow$ \texttt{S226}, \texttt{]} $\rightarrow$ \texttt{R78}, \texttt{+} $\rightarrow$ \texttt{R78}, \texttt{/} $\rightarrow$ \texttt{R78}, \texttt{\%} $\rightarrow$ \texttt{R78}, \texttt{-} $\rightarrow$ \texttt{R78} & \texttt{Factor\_Designator} $\rightarrow$ 225, \texttt{ActPars} $\rightarrow$ 227 \\ \hline
162 & \texttt{ident} $\rightarrow$ \texttt{S228} & None \\ \hline
163 & \texttt{(} $\rightarrow$ \texttt{R84}, \texttt{=} $\rightarrow$ \texttt{R84}, \texttt{[} $\rightarrow$ \texttt{S92}, \texttt{.} $\rightarrow$ \texttt{S94} & \texttt{Designator\_Tail} $\rightarrow$ 229 \\ \hline
164 & \texttt{=} $\rightarrow$ \texttt{R82}, \texttt{(} $\rightarrow$ \texttt{R82} & None \\ \hline
165 & \texttt{>=} $\rightarrow$ \texttt{R73}, \texttt{==} $\rightarrow$ \texttt{R73}, \texttt{-} $\rightarrow$ \texttt{R73}, \texttt{>} $\rightarrow$ \texttt{R73}, \texttt{*} $\rightarrow$ \texttt{R73}, \texttt{+} $\rightarrow$ \texttt{R73}, \texttt{/} $\rightarrow$ \texttt{R73}, \texttt{<=} $\rightarrow$ \texttt{R73}, \texttt{<} $\rightarrow$ \texttt{R73}, \texttt{!=} $\rightarrow$ \texttt{R73}, \texttt{\%} $\rightarrow$ \texttt{R73} & None \\ \hline
166 & \texttt{!=} $\rightarrow$ \texttt{R63}, \texttt{-} $\rightarrow$ \texttt{S138}, \texttt{+} $\rightarrow$ \texttt{S137}, \texttt{>} $\rightarrow$ \texttt{R63}, \texttt{<=} $\rightarrow$ \texttt{R63}, \texttt{<} $\rightarrow$ \texttt{R63}, \texttt{>=} $\rightarrow$ \texttt{R63}, \texttt{==} $\rightarrow$ \texttt{R63} & \texttt{Addop} $\rightarrow$ 230, \texttt{Expr\_Tail} $\rightarrow$ 231 \\ \hline
167 & \texttt{-} $\rightarrow$ \texttt{S88}, \texttt{charConst} $\rightarrow$ \texttt{R61}, \texttt{(} $\rightarrow$ \texttt{R61}, \texttt{new} $\rightarrow$ \texttt{R61}, \texttt{number} $\rightarrow$ \texttt{R61}, \texttt{ident} $\rightarrow$ \texttt{R61} & \texttt{Expr\_Minus} $\rightarrow$ 141, \texttt{Expr} $\rightarrow$ 232 \\ \hline
168 & \texttt{*} $\rightarrow$ \texttt{R74}, \texttt{+} $\rightarrow$ \texttt{R74}, \texttt{<} $\rightarrow$ \texttt{R74}, \texttt{/} $\rightarrow$ \texttt{R74}, \texttt{<=} $\rightarrow$ \texttt{R74}, \texttt{!=} $\rightarrow$ \texttt{R74}, \texttt{\%} $\rightarrow$ \texttt{R74}, \texttt{>=} $\rightarrow$ \texttt{R74}, \texttt{-} $\rightarrow$ \texttt{R74}, \texttt{>} $\rightarrow$ \texttt{R74}, \texttt{==} $\rightarrow$ \texttt{R74} & None \\ \hline
169 & \texttt{*} $\rightarrow$ \texttt{S143}, \texttt{/} $\rightarrow$ \texttt{S144}, \texttt{<=} $\rightarrow$ \texttt{R68}, \texttt{>=} $\rightarrow$ \texttt{R68}, \texttt{==} $\rightarrow$ \texttt{R68}, \texttt{\%} $\rightarrow$ \texttt{S145}, \texttt{-} $\rightarrow$ \texttt{R68}, \texttt{>} $\rightarrow$ \texttt{R68}, \texttt{<} $\rightarrow$ \texttt{R68}, \texttt{+} $\rightarrow$ \texttt{R68}, \texttt{!=} $\rightarrow$ \texttt{R68} & \texttt{Term\_Tail} $\rightarrow$ 233, \texttt{Mulop} $\rightarrow$ 234 \\ \hline
170 & \texttt{[} $\rightarrow$ \texttt{S236}, \texttt{*} $\rightarrow$ \texttt{R84}, \texttt{.} $\rightarrow$ \texttt{S235}, \texttt{<=} $\rightarrow$ \texttt{R84}, \texttt{>=} $\rightarrow$ \texttt{R84}, \texttt{==} $\rightarrow$ \texttt{R84}, \texttt{(} $\rightarrow$ \texttt{R84}, \texttt{-} $\rightarrow$ \texttt{R84}, \texttt{>} $\rightarrow$ \texttt{R84}, \texttt{<} $\rightarrow$ \texttt{R84}, \texttt{+} $\rightarrow$ \texttt{R84}, \texttt{/} $\rightarrow$ \texttt{R84}, \texttt{!=} $\rightarrow$ \texttt{R84}, \texttt{\%} $\rightarrow$ \texttt{R84} & \texttt{Designator\_Tail} $\rightarrow$ 237 \\ \hline
171 & \texttt{>=} $\rightarrow$ \texttt{R78}, \texttt{==} $\rightarrow$ \texttt{R78}, \texttt{(} $\rightarrow$ \texttt{S239}, \texttt{-} $\rightarrow$ \texttt{R78}, \texttt{>} $\rightarrow$ \texttt{R78}, \texttt{<} $\rightarrow$ \texttt{R78}, \texttt{*} $\rightarrow$ \texttt{R78}, \texttt{+} $\rightarrow$ \texttt{R78}, \texttt{/} $\rightarrow$ \texttt{R78}, \texttt{!=} $\rightarrow$ \texttt{R78}, \texttt{\%} $\rightarrow$ \texttt{R78}, \texttt{<=} $\rightarrow$ \texttt{R78} & \texttt{Factor\_Designator} $\rightarrow$ 238, \texttt{ActPars} $\rightarrow$ 240 \\ \hline
172 & \texttt{ident} $\rightarrow$ \texttt{S241} & None \\ \hline
173 & \texttt{read} $\rightarrow$ \texttt{S76}, \texttt{print} $\rightarrow$ \texttt{S77}, \texttt{if} $\rightarrow$ \texttt{S78}, \texttt{while} $\rightarrow$ \texttt{S74}, \texttt{\{} $\rightarrow$ \texttt{S68}, \texttt{;} $\rightarrow$ \texttt{S67}, \texttt{return} $\rightarrow$ \texttt{S70}, \texttt{ident} $\rightarrow$ \texttt{S73} & \texttt{Designator} $\rightarrow$ 69, \texttt{Block} $\rightarrow$ 75, \texttt{Statement} $\rightarrow$ 242 \\ \hline
174 & \texttt{number} $\rightarrow$ \texttt{R58}, \texttt{new} $\rightarrow$ \texttt{R58}, \texttt{ident} $\rightarrow$ \texttt{R58}, \texttt{(} $\rightarrow$ \texttt{R58}, \texttt{charConst} $\rightarrow$ \texttt{R58}, \texttt{-} $\rightarrow$ \texttt{R58} & None \\ \hline
175 & \texttt{-} $\rightarrow$ \texttt{S88}, \texttt{number} $\rightarrow$ \texttt{R61}, \texttt{charConst} $\rightarrow$ \texttt{R61}, \texttt{ident} $\rightarrow$ \texttt{R61}, \texttt{(} $\rightarrow$ \texttt{R61}, \texttt{new} $\rightarrow$ \texttt{R61} & \texttt{Expr\_Minus} $\rightarrow$ 141, \texttt{Expr} $\rightarrow$ 243 \\ \hline
176 & \texttt{ident} $\rightarrow$ \texttt{R53}, \texttt{new} $\rightarrow$ \texttt{R53}, \texttt{(} $\rightarrow$ \texttt{R53}, \texttt{charConst} $\rightarrow$ \texttt{R53}, \texttt{-} $\rightarrow$ \texttt{R53}, \texttt{number} $\rightarrow$ \texttt{R53} & None \\ \hline
177 & \texttt{(} $\rightarrow$ \texttt{R54}, \texttt{ident} $\rightarrow$ \texttt{R54}, \texttt{new} $\rightarrow$ \texttt{R54}, \texttt{charConst} $\rightarrow$ \texttt{R54}, \texttt{-} $\rightarrow$ \texttt{R54}, \texttt{number} $\rightarrow$ \texttt{R54} & None \\ \hline
178 & \texttt{new} $\rightarrow$ \texttt{R55}, \texttt{-} $\rightarrow$ \texttt{R55}, \texttt{ident} $\rightarrow$ \texttt{R55}, \texttt{(} $\rightarrow$ \texttt{R55}, \texttt{charConst} $\rightarrow$ \texttt{R55}, \texttt{number} $\rightarrow$ \texttt{R55} & None \\ \hline
179 & \texttt{new} $\rightarrow$ \texttt{R56}, \texttt{-} $\rightarrow$ \texttt{R56}, \texttt{ident} $\rightarrow$ \texttt{R56}, \texttt{(} $\rightarrow$ \texttt{R56}, \texttt{number} $\rightarrow$ \texttt{R56}, \texttt{charConst} $\rightarrow$ \texttt{R56} & None \\ \hline
180 & \texttt{ident} $\rightarrow$ \texttt{R57}, \texttt{(} $\rightarrow$ \texttt{R57}, \texttt{charConst} $\rightarrow$ \texttt{R57}, \texttt{number} $\rightarrow$ \texttt{R57}, \texttt{new} $\rightarrow$ \texttt{R57}, \texttt{-} $\rightarrow$ \texttt{R57} & None \\ \hline
181 & \texttt{;} $\rightarrow$ \texttt{S244} & None \\ \hline
182 & \texttt{ident} $\rightarrow$ \texttt{S245} & None \\ \hline
183 & \texttt{-} $\rightarrow$ \texttt{S88}, \texttt{number} $\rightarrow$ \texttt{R61}, \texttt{charConst} $\rightarrow$ \texttt{R61}, \texttt{ident} $\rightarrow$ \texttt{R61}, \texttt{(} $\rightarrow$ \texttt{R61}, \texttt{new} $\rightarrow$ \texttt{R61} & \texttt{Expr\_Minus} $\rightarrow$ 115, \texttt{Expr} $\rightarrow$ 246 \\ \hline
184 & \texttt{)} $\rightarrow$ \texttt{R81} & None \\ \hline
185 & \texttt{number} $\rightarrow$ \texttt{S247} & None \\ \hline
186 & \texttt{)} $\rightarrow$ \texttt{S248} & None \\ \hline
187 & \texttt{read} $\rightarrow$ \texttt{S256}, \texttt{print} $\rightarrow$ \texttt{S257}, \texttt{if} $\rightarrow$ \texttt{S253}, \texttt{while} $\rightarrow$ \texttt{S254}, \texttt{\{} $\rightarrow$ \texttt{S250}, \texttt{;} $\rightarrow$ \texttt{S249}, \texttt{return} $\rightarrow$ \texttt{S252}, \texttt{ident} $\rightarrow$ \texttt{S73} & \texttt{Designator} $\rightarrow$ 251, \texttt{Block} $\rightarrow$ 255, \texttt{Statement} $\rightarrow$ 258 \\ \hline
188 & \texttt{(} $\rightarrow$ \texttt{S127}, \texttt{new} $\rightarrow$ \texttt{S132}, \texttt{charConst} $\rightarrow$ \texttt{S128}, \texttt{number} $\rightarrow$ \texttt{S125}, \texttt{ident} $\rightarrow$ \texttt{S130} & \texttt{Term} $\rightarrow$ 259, \texttt{Factor} $\rightarrow$ 129, \texttt{Designator} $\rightarrow$ 131 \\ \hline
189 & \texttt{,} $\rightarrow$ \texttt{R59}, \texttt{)} $\rightarrow$ \texttt{R59} & None \\ \hline
190 & \texttt{)} $\rightarrow$ \texttt{S260} & None \\ \hline
191 & \texttt{+} $\rightarrow$ \texttt{R66}, \texttt{)} $\rightarrow$ \texttt{R66}, \texttt{-} $\rightarrow$ \texttt{R66}, \texttt{,} $\rightarrow$ \texttt{R66} & None \\ \hline
192 & \texttt{(} $\rightarrow$ \texttt{S127}, \texttt{new} $\rightarrow$ \texttt{S132}, \texttt{charConst} $\rightarrow$ \texttt{S128}, \texttt{number} $\rightarrow$ \texttt{S125}, \texttt{ident} $\rightarrow$ \texttt{S130} & \texttt{Factor} $\rightarrow$ 261, \texttt{Designator} $\rightarrow$ 131 \\ \hline
193 & \texttt{ident} $\rightarrow$ \texttt{S262} & None \\ \hline
194 & \texttt{-} $\rightarrow$ \texttt{S88}, \texttt{charConst} $\rightarrow$ \texttt{R61}, \texttt{(} $\rightarrow$ \texttt{R61}, \texttt{new} $\rightarrow$ \texttt{R61}, \texttt{number} $\rightarrow$ \texttt{R61}, \texttt{ident} $\rightarrow$ \texttt{R61} & \texttt{Expr\_Minus} $\rightarrow$ 115, \texttt{Expr} $\rightarrow$ 263 \\ \hline
195 & \texttt{-} $\rightarrow$ \texttt{R81}, \texttt{*} $\rightarrow$ \texttt{R81}, \texttt{+} $\rightarrow$ \texttt{R81}, \texttt{/} $\rightarrow$ \texttt{R81}, \texttt{,} $\rightarrow$ \texttt{R81}, \texttt{\%} $\rightarrow$ \texttt{R81}, \texttt{)} $\rightarrow$ \texttt{R81}, \texttt{(} $\rightarrow$ \texttt{R81} & None \\ \hline
196 & \texttt{)} $\rightarrow$ \texttt{R72}, \texttt{*} $\rightarrow$ \texttt{R72}, \texttt{+} $\rightarrow$ \texttt{R72}, \texttt{/} $\rightarrow$ \texttt{R72}, \texttt{,} $\rightarrow$ \texttt{R72}, \texttt{\%} $\rightarrow$ \texttt{R72}, \texttt{-} $\rightarrow$ \texttt{R72} & None \\ \hline
197 & \texttt{-} $\rightarrow$ \texttt{S88}, \texttt{charConst} $\rightarrow$ \texttt{R61}, \texttt{(} $\rightarrow$ \texttt{R61}, \texttt{new} $\rightarrow$ \texttt{R61}, \texttt{)} $\rightarrow$ \texttt{R49}, \texttt{number} $\rightarrow$ \texttt{R61}, \texttt{ident} $\rightarrow$ \texttt{R61} & \texttt{Expr\_Minus} $\rightarrow$ 101, \texttt{ActPars\_List} $\rightarrow$ 264, \texttt{Expr} $\rightarrow$ 103 \\ \hline
198 & \texttt{-} $\rightarrow$ \texttt{R77}, \texttt{)} $\rightarrow$ \texttt{R77}, \texttt{*} $\rightarrow$ \texttt{R77}, \texttt{+} $\rightarrow$ \texttt{R77}, \texttt{/} $\rightarrow$ \texttt{R77}, \texttt{,} $\rightarrow$ \texttt{R77}, \texttt{\%} $\rightarrow$ \texttt{R77} & None \\ \hline
199 & \texttt{[} $\rightarrow$ \texttt{S265}, \texttt{*} $\rightarrow$ \texttt{R80}, \texttt{,} $\rightarrow$ \texttt{R80}, \texttt{+} $\rightarrow$ \texttt{R80}, \texttt{/} $\rightarrow$ \texttt{R80}, \texttt{\%} $\rightarrow$ \texttt{R80}, \texttt{-} $\rightarrow$ \texttt{R80}, \texttt{)} $\rightarrow$ \texttt{R80} & \texttt{Factor\_New} $\rightarrow$ 266 \\ \hline
200 & \texttt{)} $\rightarrow$ \texttt{R51}, \texttt{,} $\rightarrow$ \texttt{S134} & \texttt{ActPars\_Tail} $\rightarrow$ 267 \\ \hline
201 & \texttt{-} $\rightarrow$ \texttt{S138}, \texttt{+} $\rightarrow$ \texttt{S137}, \texttt{;} $\rightarrow$ \texttt{R63} & \texttt{Addop} $\rightarrow$ 139, \texttt{Expr\_Tail} $\rightarrow$ 268 \\ \hline
202 & \texttt{)} $\rightarrow$ \texttt{R73}, \texttt{*} $\rightarrow$ \texttt{R73}, \texttt{+} $\rightarrow$ \texttt{R73}, \texttt{/} $\rightarrow$ \texttt{R73}, \texttt{-} $\rightarrow$ \texttt{R73}, \texttt{\%} $\rightarrow$ \texttt{R73} & None \\ \hline
203 & \texttt{-} $\rightarrow$ \texttt{S138}, \texttt{+} $\rightarrow$ \texttt{S137}, \texttt{)} $\rightarrow$ \texttt{R63} & \texttt{Addop} $\rightarrow$ 269, \texttt{Expr\_Tail} $\rightarrow$ 270 \\ \hline
204 & \texttt{-} $\rightarrow$ \texttt{S88}, \texttt{charConst} $\rightarrow$ \texttt{R61}, \texttt{(} $\rightarrow$ \texttt{R61}, \texttt{new} $\rightarrow$ \texttt{R61}, \texttt{number} $\rightarrow$ \texttt{R61}, \texttt{ident} $\rightarrow$ \texttt{R61} & \texttt{Expr\_Minus} $\rightarrow$ 141, \texttt{Expr} $\rightarrow$ 271 \\ \hline
205 & \texttt{*} $\rightarrow$ \texttt{R74}, \texttt{+} $\rightarrow$ \texttt{R74}, \texttt{\%} $\rightarrow$ \texttt{R74}, \texttt{-} $\rightarrow$ \texttt{R74}, \texttt{)} $\rightarrow$ \texttt{R74}, \texttt{/} $\rightarrow$ \texttt{R74} & None \\ \hline
206 & \texttt{*} $\rightarrow$ \texttt{S143}, \texttt{/} $\rightarrow$ \texttt{S144}, \texttt{\%} $\rightarrow$ \texttt{S145}, \texttt{+} $\rightarrow$ \texttt{R68}, \texttt{-} $\rightarrow$ \texttt{R68}, \texttt{)} $\rightarrow$ \texttt{R68} & \texttt{Term\_Tail} $\rightarrow$ 272, \texttt{Mulop} $\rightarrow$ 273 \\ \hline
207 & \texttt{)} $\rightarrow$ \texttt{R84}, \texttt{[} $\rightarrow$ \texttt{S274}, \texttt{.} $\rightarrow$ \texttt{S276}, \texttt{*} $\rightarrow$ \texttt{R84}, \texttt{(} $\rightarrow$ \texttt{R84}, \texttt{-} $\rightarrow$ \texttt{R84}, \texttt{+} $\rightarrow$ \texttt{R84}, \texttt{/} $\rightarrow$ \texttt{R84}, \texttt{\%} $\rightarrow$ \texttt{R84} & \texttt{Designator\_Tail} $\rightarrow$ 275 \\ \hline
208 & \texttt{*} $\rightarrow$ \texttt{R78}, \texttt{(} $\rightarrow$ \texttt{S278}, \texttt{+} $\rightarrow$ \texttt{R78}, \texttt{/} $\rightarrow$ \texttt{R78}, \texttt{\%} $\rightarrow$ \texttt{R78}, \texttt{-} $\rightarrow$ \texttt{R78}, \texttt{)} $\rightarrow$ \texttt{R78} & \texttt{Factor\_Designator} $\rightarrow$ 277, \texttt{ActPars} $\rightarrow$ 279 \\ \hline
209 & \texttt{ident} $\rightarrow$ \texttt{S280} & None \\ \hline
210 & \texttt{\%} $\rightarrow$ \texttt{R76}, \texttt{/} $\rightarrow$ \texttt{R76}, \texttt{;} $\rightarrow$ \texttt{R76}, \texttt{*} $\rightarrow$ \texttt{R76}, \texttt{+} $\rightarrow$ \texttt{R76}, \texttt{-} $\rightarrow$ \texttt{R76} & None \\ \hline
211 & \texttt{*} $\rightarrow$ \texttt{S143}, \texttt{/} $\rightarrow$ \texttt{S144}, \texttt{\%} $\rightarrow$ \texttt{S145}, \texttt{;} $\rightarrow$ \texttt{R68}, \texttt{+} $\rightarrow$ \texttt{R68}, \texttt{-} $\rightarrow$ \texttt{R68} & \texttt{Term\_Tail} $\rightarrow$ 281, \texttt{Mulop} $\rightarrow$ 147 \\ \hline
212 & \texttt{]} $\rightarrow$ \texttt{S282} & None \\ \hline
213 & \texttt{[} $\rightarrow$ \texttt{S148}, \texttt{.} $\rightarrow$ \texttt{S150}, \texttt{*} $\rightarrow$ \texttt{R84}, \texttt{;} $\rightarrow$ \texttt{R84}, \texttt{(} $\rightarrow$ \texttt{R84}, \texttt{+} $\rightarrow$ \texttt{R84}, \texttt{/} $\rightarrow$ \texttt{R84}, \texttt{\%} $\rightarrow$ \texttt{R84}, \texttt{-} $\rightarrow$ \texttt{R84} & \texttt{Designator\_Tail} $\rightarrow$ 283 \\ \hline
214 & \texttt{)} $\rightarrow$ \texttt{S284} & None \\ \hline
215 & \texttt{-} $\rightarrow$ \texttt{S88}, \texttt{charConst} $\rightarrow$ \texttt{R61}, \texttt{(} $\rightarrow$ \texttt{R61}, \texttt{new} $\rightarrow$ \texttt{R61}, \texttt{number} $\rightarrow$ \texttt{R61}, \texttt{ident} $\rightarrow$ \texttt{R61} & \texttt{Expr\_Minus} $\rightarrow$ 115, \texttt{Expr} $\rightarrow$ 285 \\ \hline
216 & \texttt{-} $\rightarrow$ \texttt{R75}, \texttt{;} $\rightarrow$ \texttt{R75}, \texttt{*} $\rightarrow$ \texttt{R75}, \texttt{+} $\rightarrow$ \texttt{R75}, \texttt{/} $\rightarrow$ \texttt{R75}, \texttt{\%} $\rightarrow$ \texttt{R75} & None \\ \hline
217 & \texttt{(} $\rightarrow$ \texttt{S157}, \texttt{new} $\rightarrow$ \texttt{S162}, \texttt{charConst} $\rightarrow$ \texttt{S158}, \texttt{ident} $\rightarrow$ \texttt{S160}, \texttt{number} $\rightarrow$ \texttt{S155} & \texttt{Term} $\rightarrow$ 286, \texttt{Factor} $\rightarrow$ 159, \texttt{Designator} $\rightarrow$ 161 \\ \hline
218 & \texttt{]} $\rightarrow$ \texttt{R59} & None \\ \hline
219 & \texttt{)} $\rightarrow$ \texttt{S287} & None \\ \hline
220 & \texttt{]} $\rightarrow$ \texttt{R66}, \texttt{+} $\rightarrow$ \texttt{R66}, \texttt{-} $\rightarrow$ \texttt{R66} & None \\ \hline
221 & \texttt{(} $\rightarrow$ \texttt{S157}, \texttt{new} $\rightarrow$ \texttt{S162}, \texttt{charConst} $\rightarrow$ \texttt{S158}, \texttt{ident} $\rightarrow$ \texttt{S160}, \texttt{number} $\rightarrow$ \texttt{S155} & \texttt{Factor} $\rightarrow$ 288, \texttt{Designator} $\rightarrow$ 161 \\ \hline
222 & \texttt{-} $\rightarrow$ \texttt{S88}, \texttt{charConst} $\rightarrow$ \texttt{R61}, \texttt{(} $\rightarrow$ \texttt{R61}, \texttt{new} $\rightarrow$ \texttt{R61}, \texttt{number} $\rightarrow$ \texttt{R61}, \texttt{ident} $\rightarrow$ \texttt{R61} & \texttt{Expr\_Minus} $\rightarrow$ 115, \texttt{Expr} $\rightarrow$ 289 \\ \hline
223 & \texttt{-} $\rightarrow$ \texttt{R81}, \texttt{+} $\rightarrow$ \texttt{R81}, \texttt{(} $\rightarrow$ \texttt{R81}, \texttt{\%} $\rightarrow$ \texttt{R81}, \texttt{*} $\rightarrow$ \texttt{R81}, \texttt{]} $\rightarrow$ \texttt{R81}, \texttt{/} $\rightarrow$ \texttt{R81} & None \\ \hline
224 & \texttt{ident} $\rightarrow$ \texttt{S290} & None \\ \hline
225 & \texttt{*} $\rightarrow$ \texttt{R72}, \texttt{]} $\rightarrow$ \texttt{R72}, \texttt{+} $\rightarrow$ \texttt{R72}, \texttt{/} $\rightarrow$ \texttt{R72}, \texttt{\%} $\rightarrow$ \texttt{R72}, \texttt{-} $\rightarrow$ \texttt{R72} & None \\ \hline
226 & \texttt{-} $\rightarrow$ \texttt{S88}, \texttt{charConst} $\rightarrow$ \texttt{R61}, \texttt{(} $\rightarrow$ \texttt{R61}, \texttt{new} $\rightarrow$ \texttt{R61}, \texttt{)} $\rightarrow$ \texttt{R49}, \texttt{number} $\rightarrow$ \texttt{R61}, \texttt{ident} $\rightarrow$ \texttt{R61} & \texttt{Expr\_Minus} $\rightarrow$ 101, \texttt{ActPars\_List} $\rightarrow$ 291, \texttt{Expr} $\rightarrow$ 103 \\ \hline
227 & \texttt{-} $\rightarrow$ \texttt{R77}, \texttt{*} $\rightarrow$ \texttt{R77}, \texttt{+} $\rightarrow$ \texttt{R77}, \texttt{]} $\rightarrow$ \texttt{R77}, \texttt{/} $\rightarrow$ \texttt{R77}, \texttt{\%} $\rightarrow$ \texttt{R77} & None \\ \hline
228 & \texttt{[} $\rightarrow$ \texttt{S292}, \texttt{*} $\rightarrow$ \texttt{R80}, \texttt{]} $\rightarrow$ \texttt{R80}, \texttt{+} $\rightarrow$ \texttt{R80}, \texttt{/} $\rightarrow$ \texttt{R80}, \texttt{\%} $\rightarrow$ \texttt{R80}, \texttt{-} $\rightarrow$ \texttt{R80} & \texttt{Factor\_New} $\rightarrow$ 293 \\ \hline
229 & \texttt{(} $\rightarrow$ \texttt{R83}, \texttt{=} $\rightarrow$ \texttt{R83} & None \\ \hline
230 & \texttt{new} $\rightarrow$ \texttt{S172}, \texttt{ident} $\rightarrow$ \texttt{S170}, \texttt{(} $\rightarrow$ \texttt{S167}, \texttt{charConst} $\rightarrow$ \texttt{S168}, \texttt{number} $\rightarrow$ \texttt{S165} & \texttt{Term} $\rightarrow$ 294, \texttt{Factor} $\rightarrow$ 169, \texttt{Designator} $\rightarrow$ 171 \\ \hline
231 & \texttt{<=} $\rightarrow$ \texttt{R59}, \texttt{>=} $\rightarrow$ \texttt{R59}, \texttt{!=} $\rightarrow$ \texttt{R59}, \texttt{<} $\rightarrow$ \texttt{R59}, \texttt{>} $\rightarrow$ \texttt{R59}, \texttt{==} $\rightarrow$ \texttt{R59} & None \\ \hline
232 & \texttt{)} $\rightarrow$ \texttt{S295} & None \\ \hline
233 & \texttt{-} $\rightarrow$ \texttt{R66}, \texttt{!=} $\rightarrow$ \texttt{R66}, \texttt{>} $\rightarrow$ \texttt{R66}, \texttt{==} $\rightarrow$ \texttt{R66}, \texttt{+} $\rightarrow$ \texttt{R66}, \texttt{<} $\rightarrow$ \texttt{R66}, \texttt{<=} $\rightarrow$ \texttt{R66}, \texttt{>=} $\rightarrow$ \texttt{R66} & None \\ \hline
234 & \texttt{new} $\rightarrow$ \texttt{S172}, \texttt{ident} $\rightarrow$ \texttt{S170}, \texttt{(} $\rightarrow$ \texttt{S167}, \texttt{charConst} $\rightarrow$ \texttt{S168}, \texttt{number} $\rightarrow$ \texttt{S165} & \texttt{Factor} $\rightarrow$ 296, \texttt{Designator} $\rightarrow$ 171 \\ \hline
235 & \texttt{ident} $\rightarrow$ \texttt{S297} & None \\ \hline
236 & \texttt{-} $\rightarrow$ \texttt{S88}, \texttt{charConst} $\rightarrow$ \texttt{R61}, \texttt{(} $\rightarrow$ \texttt{R61}, \texttt{new} $\rightarrow$ \texttt{R61}, \texttt{number} $\rightarrow$ \texttt{R61}, \texttt{ident} $\rightarrow$ \texttt{R61} & \texttt{Expr\_Minus} $\rightarrow$ 115, \texttt{Expr} $\rightarrow$ 298 \\ \hline
237 & \texttt{-} $\rightarrow$ \texttt{R81}, \texttt{>} $\rightarrow$ \texttt{R81}, \texttt{==} $\rightarrow$ \texttt{R81}, \texttt{*} $\rightarrow$ \texttt{R81}, \texttt{+} $\rightarrow$ \texttt{R81}, \texttt{/} $\rightarrow$ \texttt{R81}, \texttt{<} $\rightarrow$ \texttt{R81}, \texttt{\%} $\rightarrow$ \texttt{R81}, \texttt{<=} $\rightarrow$ \texttt{R81}, \texttt{>=} $\rightarrow$ \texttt{R81}, \texttt{!=} $\rightarrow$ \texttt{R81}, \texttt{(} $\rightarrow$ \texttt{R81} & None \\ \hline
238 & \texttt{>} $\rightarrow$ \texttt{R72}, \texttt{==} $\rightarrow$ \texttt{R72}, \texttt{<} $\rightarrow$ \texttt{R72}, \texttt{*} $\rightarrow$ \texttt{R72}, \texttt{+} $\rightarrow$ \texttt{R72}, \texttt{/} $\rightarrow$ \texttt{R72}, \texttt{<=} $\rightarrow$ \texttt{R72}, \texttt{>=} $\rightarrow$ \texttt{R72}, \texttt{!=} $\rightarrow$ \texttt{R72}, \texttt{\%} $\rightarrow$ \texttt{R72}, \texttt{-} $\rightarrow$ \texttt{R72} & None \\ \hline
239 & \texttt{-} $\rightarrow$ \texttt{S88}, \texttt{charConst} $\rightarrow$ \texttt{R61}, \texttt{(} $\rightarrow$ \texttt{R61}, \texttt{new} $\rightarrow$ \texttt{R61}, \texttt{)} $\rightarrow$ \texttt{R49}, \texttt{number} $\rightarrow$ \texttt{R61}, \texttt{ident} $\rightarrow$ \texttt{R61} & \texttt{Expr\_Minus} $\rightarrow$ 101, \texttt{ActPars\_List} $\rightarrow$ 299, \texttt{Expr} $\rightarrow$ 103 \\ \hline
240 & \texttt{<} $\rightarrow$ \texttt{R77}, \texttt{*} $\rightarrow$ \texttt{R77}, \texttt{+} $\rightarrow$ \texttt{R77}, \texttt{/} $\rightarrow$ \texttt{R77}, \texttt{<=} $\rightarrow$ \texttt{R77}, \texttt{!=} $\rightarrow$ \texttt{R77}, \texttt{\%} $\rightarrow$ \texttt{R77}, \texttt{-} $\rightarrow$ \texttt{R77}, \texttt{>=} $\rightarrow$ \texttt{R77}, \texttt{>} $\rightarrow$ \texttt{R77}, \texttt{==} $\rightarrow$ \texttt{R77} & None \\ \hline
241 & \texttt{*} $\rightarrow$ \texttt{R80}, \texttt{[} $\rightarrow$ \texttt{S300}, \texttt{<=} $\rightarrow$ \texttt{R80}, \texttt{>=} $\rightarrow$ \texttt{R80}, \texttt{==} $\rightarrow$ \texttt{R80}, \texttt{-} $\rightarrow$ \texttt{R80}, \texttt{>} $\rightarrow$ \texttt{R80}, \texttt{<} $\rightarrow$ \texttt{R80}, \texttt{+} $\rightarrow$ \texttt{R80}, \texttt{/} $\rightarrow$ \texttt{R80}, \texttt{!=} $\rightarrow$ \texttt{R80}, \texttt{\%} $\rightarrow$ \texttt{R80} & \texttt{Factor\_New} $\rightarrow$ 301 \\ \hline
242 & \texttt{if} $\rightarrow$ \texttt{R33}, \texttt{print} $\rightarrow$ \texttt{R33}, \texttt{\}} $\rightarrow$ \texttt{R33}, \texttt{;} $\rightarrow$ \texttt{R33}, \texttt{read} $\rightarrow$ \texttt{R33}, \texttt{\{} $\rightarrow$ \texttt{R33}, \texttt{ident} $\rightarrow$ \texttt{R33}, \texttt{while} $\rightarrow$ \texttt{R33}, \texttt{return} $\rightarrow$ \texttt{R33} & None \\ \hline
243 & \texttt{)} $\rightarrow$ \texttt{R52} & None \\ \hline
244 & \texttt{read} $\rightarrow$ \texttt{R35}, \texttt{\{} $\rightarrow$ \texttt{R35}, \texttt{while} $\rightarrow$ \texttt{R35}, \texttt{ident} $\rightarrow$ \texttt{R35}, \texttt{;} $\rightarrow$ \texttt{R35}, \texttt{print} $\rightarrow$ \texttt{R35}, \texttt{return} $\rightarrow$ \texttt{R35}, \texttt{if} $\rightarrow$ \texttt{R35}, \texttt{\}} $\rightarrow$ \texttt{R35} & None \\ \hline
245 & \texttt{)} $\rightarrow$ \texttt{R84}, \texttt{.} $\rightarrow$ \texttt{S182}, \texttt{[} $\rightarrow$ \texttt{S183} & \texttt{Designator\_Tail} $\rightarrow$ 302 \\ \hline
246 & \texttt{]} $\rightarrow$ \texttt{S303} & None \\ \hline
247 & \texttt{)} $\rightarrow$ \texttt{R45} & None \\ \hline
248 & \texttt{;} $\rightarrow$ \texttt{S304} & None \\ \hline
249 & \texttt{read} $\rightarrow$ \texttt{R38}, \texttt{\}} $\rightarrow$ \texttt{R38}, \texttt{\{} $\rightarrow$ \texttt{R38}, \texttt{return} $\rightarrow$ \texttt{R38}, \texttt{ident} $\rightarrow$ \texttt{R38}, \texttt{;} $\rightarrow$ \texttt{R38}, \texttt{while} $\rightarrow$ \texttt{R38}, \texttt{else} $\rightarrow$ \texttt{R38}, \texttt{if} $\rightarrow$ \texttt{R38}, \texttt{print} $\rightarrow$ \texttt{R38} & None \\ \hline
250 & \texttt{read} $\rightarrow$ \texttt{S76}, \texttt{print} $\rightarrow$ \texttt{S77}, \texttt{if} $\rightarrow$ \texttt{S78}, \texttt{while} $\rightarrow$ \texttt{S74}, \texttt{\{} $\rightarrow$ \texttt{S68}, \texttt{;} $\rightarrow$ \texttt{S67}, \texttt{return} $\rightarrow$ \texttt{S70}, \texttt{\}} $\rightarrow$ \texttt{R30}, \texttt{ident} $\rightarrow$ \texttt{S73} & \texttt{Designator} $\rightarrow$ 69, \texttt{Statements} $\rightarrow$ 305, \texttt{Statement} $\rightarrow$ 72, \texttt{Block} $\rightarrow$ 75 \\ \hline
251 & \texttt{=} $\rightarrow$ \texttt{S307}, \texttt{(} $\rightarrow$ \texttt{S83} & \texttt{Statement\_AssignOrCall} $\rightarrow$ 306, \texttt{ActPars} $\rightarrow$ 308 \\ \hline
252 & \texttt{-} $\rightarrow$ \texttt{S88}, \texttt{charConst} $\rightarrow$ \texttt{R61}, \texttt{;} $\rightarrow$ \texttt{R44}, \texttt{(} $\rightarrow$ \texttt{R61}, \texttt{new} $\rightarrow$ \texttt{R61}, \texttt{number} $\rightarrow$ \texttt{R61}, \texttt{ident} $\rightarrow$ \texttt{R61} & \texttt{Expr\_Minus} $\rightarrow$ 86, \texttt{Expr} $\rightarrow$ 87, \texttt{Expr\_Opt} $\rightarrow$ 309 \\ \hline
253 & \texttt{(} $\rightarrow$ \texttt{S310} & None \\ \hline
254 & \texttt{(} $\rightarrow$ \texttt{S311} & None \\ \hline
255 & \texttt{\{} $\rightarrow$ \texttt{R37}, \texttt{;} $\rightarrow$ \texttt{R37}, \texttt{while} $\rightarrow$ \texttt{R37}, \texttt{ident} $\rightarrow$ \texttt{R37}, \texttt{else} $\rightarrow$ \texttt{R37}, \texttt{print} $\rightarrow$ \texttt{R37}, \texttt{return} $\rightarrow$ \texttt{R37}, \texttt{\}} $\rightarrow$ \texttt{R37}, \texttt{if} $\rightarrow$ \texttt{R37}, \texttt{read} $\rightarrow$ \texttt{R37} & None \\ \hline
256 & \texttt{(} $\rightarrow$ \texttt{S312} & None \\ \hline
257 & \texttt{(} $\rightarrow$ \texttt{S313} & None \\ \hline
258 & \texttt{return} $\rightarrow$ \texttt{R42}, \texttt{else} $\rightarrow$ \texttt{S315}, \texttt{if} $\rightarrow$ \texttt{R42}, \texttt{read} $\rightarrow$ \texttt{R42}, \texttt{\{} $\rightarrow$ \texttt{R42}, \texttt{ident} $\rightarrow$ \texttt{R42}, \texttt{print} $\rightarrow$ \texttt{R42}, \texttt{while} $\rightarrow$ \texttt{R42}, \texttt{;} $\rightarrow$ \texttt{R42}, \texttt{\}} $\rightarrow$ \texttt{R42} & \texttt{Else\_Opt} $\rightarrow$ 314 \\ \hline
259 & \texttt{-} $\rightarrow$ \texttt{S138}, \texttt{)} $\rightarrow$ \texttt{R63}, \texttt{+} $\rightarrow$ \texttt{S137}, \texttt{,} $\rightarrow$ \texttt{R63} & \texttt{Addop} $\rightarrow$ 188, \texttt{Expr\_Tail} $\rightarrow$ 316 \\ \hline
260 & \texttt{)} $\rightarrow$ \texttt{R76}, \texttt{\%} $\rightarrow$ \texttt{R76}, \texttt{/} $\rightarrow$ \texttt{R76}, \texttt{,} $\rightarrow$ \texttt{R76}, \texttt{*} $\rightarrow$ \texttt{R76}, \texttt{+} $\rightarrow$ \texttt{R76}, \texttt{-} $\rightarrow$ \texttt{R76} & None \\ \hline
261 & \texttt{*} $\rightarrow$ \texttt{S143}, \texttt{/} $\rightarrow$ \texttt{S144}, \texttt{\%} $\rightarrow$ \texttt{S145}, \texttt{,} $\rightarrow$ \texttt{R68}, \texttt{+} $\rightarrow$ \texttt{R68}, \texttt{-} $\rightarrow$ \texttt{R68}, \texttt{)} $\rightarrow$ \texttt{R68} & \texttt{Term\_Tail} $\rightarrow$ 317, \texttt{Mulop} $\rightarrow$ 192 \\ \hline
262 & \texttt{)} $\rightarrow$ \texttt{R84}, \texttt{[} $\rightarrow$ \texttt{S194}, \texttt{*} $\rightarrow$ \texttt{R84}, \texttt{.} $\rightarrow$ \texttt{S193}, \texttt{(} $\rightarrow$ \texttt{R84}, \texttt{-} $\rightarrow$ \texttt{R84}, \texttt{,} $\rightarrow$ \texttt{R84}, \texttt{+} $\rightarrow$ \texttt{R84}, \texttt{/} $\rightarrow$ \texttt{R84}, \texttt{\%} $\rightarrow$ \texttt{R84} & \texttt{Designator\_Tail} $\rightarrow$ 318 \\ \hline
263 & \texttt{]} $\rightarrow$ \texttt{S319} & None \\ \hline
264 & \texttt{)} $\rightarrow$ \texttt{S320} & None \\ \hline
265 & \texttt{-} $\rightarrow$ \texttt{S88}, \texttt{charConst} $\rightarrow$ \texttt{R61}, \texttt{(} $\rightarrow$ \texttt{R61}, \texttt{new} $\rightarrow$ \texttt{R61}, \texttt{number} $\rightarrow$ \texttt{R61}, \texttt{ident} $\rightarrow$ \texttt{R61} & \texttt{Expr\_Minus} $\rightarrow$ 115, \texttt{Expr} $\rightarrow$ 321 \\ \hline
266 & \texttt{-} $\rightarrow$ \texttt{R75}, \texttt{)} $\rightarrow$ \texttt{R75}, \texttt{*} $\rightarrow$ \texttt{R75}, \texttt{+} $\rightarrow$ \texttt{R75}, \texttt{/} $\rightarrow$ \texttt{R75}, \texttt{,} $\rightarrow$ \texttt{R75}, \texttt{\%} $\rightarrow$ \texttt{R75} & None \\ \hline
267 & \texttt{)} $\rightarrow$ \texttt{R50} & None \\ \hline
268 & \texttt{;} $\rightarrow$ \texttt{R62} & None \\ \hline
269 & \texttt{(} $\rightarrow$ \texttt{S204}, \texttt{new} $\rightarrow$ \texttt{S209}, \texttt{charConst} $\rightarrow$ \texttt{S205}, \texttt{ident} $\rightarrow$ \texttt{S207}, \texttt{number} $\rightarrow$ \texttt{S202} & \texttt{Term} $\rightarrow$ 322, \texttt{Factor} $\rightarrow$ 206, \texttt{Designator} $\rightarrow$ 208 \\ \hline
270 & \texttt{)} $\rightarrow$ \texttt{R59} & None \\ \hline
271 & \texttt{)} $\rightarrow$ \texttt{S323} & None \\ \hline
272 & \texttt{+} $\rightarrow$ \texttt{R66}, \texttt{-} $\rightarrow$ \texttt{R66}, \texttt{)} $\rightarrow$ \texttt{R66} & None \\ \hline
273 & \texttt{(} $\rightarrow$ \texttt{S204}, \texttt{new} $\rightarrow$ \texttt{S209}, \texttt{charConst} $\rightarrow$ \texttt{S205}, \texttt{ident} $\rightarrow$ \texttt{S207}, \texttt{number} $\rightarrow$ \texttt{S202} & \texttt{Factor} $\rightarrow$ 324, \texttt{Designator} $\rightarrow$ 208 \\ \hline
274 & \texttt{-} $\rightarrow$ \texttt{S88}, \texttt{charConst} $\rightarrow$ \texttt{R61}, \texttt{(} $\rightarrow$ \texttt{R61}, \texttt{new} $\rightarrow$ \texttt{R61}, \texttt{number} $\rightarrow$ \texttt{R61}, \texttt{ident} $\rightarrow$ \texttt{R61} & \texttt{Expr\_Minus} $\rightarrow$ 115, \texttt{Expr} $\rightarrow$ 325 \\ \hline
275 & \texttt{-} $\rightarrow$ \texttt{R81}, \texttt{(} $\rightarrow$ \texttt{R81}, \texttt{\%} $\rightarrow$ \texttt{R81}, \texttt{)} $\rightarrow$ \texttt{R81}, \texttt{*} $\rightarrow$ \texttt{R81}, \texttt{+} $\rightarrow$ \texttt{R81}, \texttt{/} $\rightarrow$ \texttt{R81} & None \\ \hline
276 & \texttt{ident} $\rightarrow$ \texttt{S326} & None \\ \hline
277 & \texttt{)} $\rightarrow$ \texttt{R72}, \texttt{*} $\rightarrow$ \texttt{R72}, \texttt{+} $\rightarrow$ \texttt{R72}, \texttt{/} $\rightarrow$ \texttt{R72}, \texttt{\%} $\rightarrow$ \texttt{R72}, \texttt{-} $\rightarrow$ \texttt{R72} & None \\ \hline
278 & \texttt{-} $\rightarrow$ \texttt{S88}, \texttt{charConst} $\rightarrow$ \texttt{R61}, \texttt{(} $\rightarrow$ \texttt{R61}, \texttt{new} $\rightarrow$ \texttt{R61}, \texttt{)} $\rightarrow$ \texttt{R49}, \texttt{number} $\rightarrow$ \texttt{R61}, \texttt{ident} $\rightarrow$ \texttt{R61} & \texttt{Expr\_Minus} $\rightarrow$ 101, \texttt{ActPars\_List} $\rightarrow$ 327, \texttt{Expr} $\rightarrow$ 103 \\ \hline
279 & \texttt{-} $\rightarrow$ \texttt{R77}, \texttt{)} $\rightarrow$ \texttt{R77}, \texttt{*} $\rightarrow$ \texttt{R77}, \texttt{+} $\rightarrow$ \texttt{R77}, \texttt{/} $\rightarrow$ \texttt{R77}, \texttt{\%} $\rightarrow$ \texttt{R77} & None \\ \hline
280 & \texttt{[} $\rightarrow$ \texttt{S328}, \texttt{*} $\rightarrow$ \texttt{R80}, \texttt{+} $\rightarrow$ \texttt{R80}, \texttt{/} $\rightarrow$ \texttt{R80}, \texttt{\%} $\rightarrow$ \texttt{R80}, \texttt{-} $\rightarrow$ \texttt{R80}, \texttt{)} $\rightarrow$ \texttt{R80} & \texttt{Factor\_New} $\rightarrow$ 329 \\ \hline
281 & \texttt{-} $\rightarrow$ \texttt{R67}, \texttt{;} $\rightarrow$ \texttt{R67}, \texttt{+} $\rightarrow$ \texttt{R67} & None \\ \hline
282 & \texttt{[} $\rightarrow$ \texttt{S148}, \texttt{.} $\rightarrow$ \texttt{S150}, \texttt{*} $\rightarrow$ \texttt{R84}, \texttt{;} $\rightarrow$ \texttt{R84}, \texttt{(} $\rightarrow$ \texttt{R84}, \texttt{-} $\rightarrow$ \texttt{R84}, \texttt{+} $\rightarrow$ \texttt{R84}, \texttt{/} $\rightarrow$ \texttt{R84}, \texttt{\%} $\rightarrow$ \texttt{R84} & \texttt{Designator\_Tail} $\rightarrow$ 330 \\ \hline
283 & \texttt{/} $\rightarrow$ \texttt{R82}, \texttt{\%} $\rightarrow$ \texttt{R82}, \texttt{+} $\rightarrow$ \texttt{R82}, \texttt{*} $\rightarrow$ \texttt{R82}, \texttt{-} $\rightarrow$ \texttt{R82}, \texttt{;} $\rightarrow$ \texttt{R82}, \texttt{(} $\rightarrow$ \texttt{R82} & None \\ \hline
284 & \texttt{;} $\rightarrow$ \texttt{R47}, \texttt{*} $\rightarrow$ \texttt{R47}, \texttt{+} $\rightarrow$ \texttt{R47}, \texttt{-} $\rightarrow$ \texttt{R47}, \texttt{\%} $\rightarrow$ \texttt{R47}, \texttt{/} $\rightarrow$ \texttt{R47} & None \\ \hline
285 & \texttt{]} $\rightarrow$ \texttt{S331} & None \\ \hline
286 & \texttt{-} $\rightarrow$ \texttt{S138}, \texttt{+} $\rightarrow$ \texttt{S137}, \texttt{]} $\rightarrow$ \texttt{R63} & \texttt{Addop} $\rightarrow$ 217, \texttt{Expr\_Tail} $\rightarrow$ 332 \\ \hline
287 & \texttt{\%} $\rightarrow$ \texttt{R76}, \texttt{/} $\rightarrow$ \texttt{R76}, \texttt{]} $\rightarrow$ \texttt{R76}, \texttt{*} $\rightarrow$ \texttt{R76}, \texttt{+} $\rightarrow$ \texttt{R76}, \texttt{-} $\rightarrow$ \texttt{R76} & None \\ \hline
288 & \texttt{*} $\rightarrow$ \texttt{S143}, \texttt{/} $\rightarrow$ \texttt{S144}, \texttt{\%} $\rightarrow$ \texttt{S145}, \texttt{]} $\rightarrow$ \texttt{R68}, \texttt{+} $\rightarrow$ \texttt{R68}, \texttt{-} $\rightarrow$ \texttt{R68} & \texttt{Term\_Tail} $\rightarrow$ 333, \texttt{Mulop} $\rightarrow$ 221 \\ \hline
289 & \texttt{]} $\rightarrow$ \texttt{S334} & None \\ \hline
290 & \texttt{[} $\rightarrow$ \texttt{S222}, \texttt{.} $\rightarrow$ \texttt{S224}, \texttt{*} $\rightarrow$ \texttt{R84}, \texttt{(} $\rightarrow$ \texttt{R84}, \texttt{]} $\rightarrow$ \texttt{R84}, \texttt{+} $\rightarrow$ \texttt{R84}, \texttt{/} $\rightarrow$ \texttt{R84}, \texttt{\%} $\rightarrow$ \texttt{R84}, \texttt{-} $\rightarrow$ \texttt{R84} & \texttt{Designator\_Tail} $\rightarrow$ 335 \\ \hline
291 & \texttt{)} $\rightarrow$ \texttt{S336} & None \\ \hline
292 & \texttt{-} $\rightarrow$ \texttt{S88}, \texttt{charConst} $\rightarrow$ \texttt{R61}, \texttt{(} $\rightarrow$ \texttt{R61}, \texttt{new} $\rightarrow$ \texttt{R61}, \texttt{number} $\rightarrow$ \texttt{R61}, \texttt{ident} $\rightarrow$ \texttt{R61} & \texttt{Expr\_Minus} $\rightarrow$ 115, \texttt{Expr} $\rightarrow$ 337 \\ \hline
293 & \texttt{-} $\rightarrow$ \texttt{R75}, \texttt{*} $\rightarrow$ \texttt{R75}, \texttt{+} $\rightarrow$ \texttt{R75}, \texttt{]} $\rightarrow$ \texttt{R75}, \texttt{/} $\rightarrow$ \texttt{R75}, \texttt{\%} $\rightarrow$ \texttt{R75} & None \\ \hline
294 & \texttt{!=} $\rightarrow$ \texttt{R63}, \texttt{-} $\rightarrow$ \texttt{S138}, \texttt{+} $\rightarrow$ \texttt{S137}, \texttt{>} $\rightarrow$ \texttt{R63}, \texttt{<=} $\rightarrow$ \texttt{R63}, \texttt{<} $\rightarrow$ \texttt{R63}, \texttt{>=} $\rightarrow$ \texttt{R63}, \texttt{==} $\rightarrow$ \texttt{R63} & \texttt{Addop} $\rightarrow$ 230, \texttt{Expr\_Tail} $\rightarrow$ 338 \\ \hline
295 & \texttt{>} $\rightarrow$ \texttt{R76}, \texttt{==} $\rightarrow$ \texttt{R76}, \texttt{*} $\rightarrow$ \texttt{R76}, \texttt{+} $\rightarrow$ \texttt{R76}, \texttt{<} $\rightarrow$ \texttt{R76}, \texttt{\%} $\rightarrow$ \texttt{R76}, \texttt{<=} $\rightarrow$ \texttt{R76}, \texttt{!=} $\rightarrow$ \texttt{R76}, \texttt{/} $\rightarrow$ \texttt{R76}, \texttt{>=} $\rightarrow$ \texttt{R76}, \texttt{-} $\rightarrow$ \texttt{R76} & None \\ \hline
296 & \texttt{*} $\rightarrow$ \texttt{S143}, \texttt{/} $\rightarrow$ \texttt{S144}, \texttt{<=} $\rightarrow$ \texttt{R68}, \texttt{>=} $\rightarrow$ \texttt{R68}, \texttt{==} $\rightarrow$ \texttt{R68}, \texttt{\%} $\rightarrow$ \texttt{S145}, \texttt{-} $\rightarrow$ \texttt{R68}, \texttt{>} $\rightarrow$ \texttt{R68}, \texttt{<} $\rightarrow$ \texttt{R68}, \texttt{+} $\rightarrow$ \texttt{R68}, \texttt{!=} $\rightarrow$ \texttt{R68} & \texttt{Term\_Tail} $\rightarrow$ 339, \texttt{Mulop} $\rightarrow$ 234 \\ \hline
297 & \texttt{[} $\rightarrow$ \texttt{S236}, \texttt{*} $\rightarrow$ \texttt{R84}, \texttt{!=} $\rightarrow$ \texttt{R84}, \texttt{.} $\rightarrow$ \texttt{S235}, \texttt{<=} $\rightarrow$ \texttt{R84}, \texttt{>=} $\rightarrow$ \texttt{R84}, \texttt{(} $\rightarrow$ \texttt{R84}, \texttt{==} $\rightarrow$ \texttt{R84}, \texttt{-} $\rightarrow$ \texttt{R84}, \texttt{>} $\rightarrow$ \texttt{R84}, \texttt{<} $\rightarrow$ \texttt{R84}, \texttt{+} $\rightarrow$ \texttt{R84}, \texttt{/} $\rightarrow$ \texttt{R84}, \texttt{\%} $\rightarrow$ \texttt{R84} & \texttt{Designator\_Tail} $\rightarrow$ 340 \\ \hline
298 & \texttt{]} $\rightarrow$ \texttt{S341} & None \\ \hline
299 & \texttt{)} $\rightarrow$ \texttt{S342} & None \\ \hline
300 & \texttt{-} $\rightarrow$ \texttt{S88}, \texttt{charConst} $\rightarrow$ \texttt{R61}, \texttt{(} $\rightarrow$ \texttt{R61}, \texttt{new} $\rightarrow$ \texttt{R61}, \texttt{number} $\rightarrow$ \texttt{R61}, \texttt{ident} $\rightarrow$ \texttt{R61} & \texttt{Expr\_Minus} $\rightarrow$ 115, \texttt{Expr} $\rightarrow$ 343 \\ \hline
301 & \texttt{>=} $\rightarrow$ \texttt{R75}, \texttt{-} $\rightarrow$ \texttt{R75}, \texttt{>} $\rightarrow$ \texttt{R75}, \texttt{==} $\rightarrow$ \texttt{R75}, \texttt{<} $\rightarrow$ \texttt{R75}, \texttt{*} $\rightarrow$ \texttt{R75}, \texttt{+} $\rightarrow$ \texttt{R75}, \texttt{/} $\rightarrow$ \texttt{R75}, \texttt{<=} $\rightarrow$ \texttt{R75}, \texttt{!=} $\rightarrow$ \texttt{R75}, \texttt{\%} $\rightarrow$ \texttt{R75} & None \\ \hline
302 & \texttt{)} $\rightarrow$ \texttt{R82} & None \\ \hline
303 & \texttt{)} $\rightarrow$ \texttt{R84}, \texttt{.} $\rightarrow$ \texttt{S182}, \texttt{[} $\rightarrow$ \texttt{S183} & \texttt{Designator\_Tail} $\rightarrow$ 344 \\ \hline
304 & \texttt{read} $\rightarrow$ \texttt{R36}, \texttt{\{} $\rightarrow$ \texttt{R36}, \texttt{ident} $\rightarrow$ \texttt{R36}, \texttt{;} $\rightarrow$ \texttt{R36}, \texttt{while} $\rightarrow$ \texttt{R36}, \texttt{print} $\rightarrow$ \texttt{R36}, \texttt{return} $\rightarrow$ \texttt{R36}, \texttt{\}} $\rightarrow$ \texttt{R36}, \texttt{if} $\rightarrow$ \texttt{R36} & None \\ \hline
305 & \texttt{\}} $\rightarrow$ \texttt{S345} & None \\ \hline
306 & \texttt{;} $\rightarrow$ \texttt{R31}, \texttt{while} $\rightarrow$ \texttt{R31}, \texttt{ident} $\rightarrow$ \texttt{R31}, \texttt{else} $\rightarrow$ \texttt{R31}, \texttt{return} $\rightarrow$ \texttt{R31}, \texttt{if} $\rightarrow$ \texttt{R31}, \texttt{\}} $\rightarrow$ \texttt{R31}, \texttt{print} $\rightarrow$ \texttt{R31}, \texttt{read} $\rightarrow$ \texttt{R31}, \texttt{\{} $\rightarrow$ \texttt{R31} & None \\ \hline
307 & \texttt{-} $\rightarrow$ \texttt{S88}, \texttt{charConst} $\rightarrow$ \texttt{R61}, \texttt{(} $\rightarrow$ \texttt{R61}, \texttt{new} $\rightarrow$ \texttt{R61}, \texttt{number} $\rightarrow$ \texttt{R61}, \texttt{ident} $\rightarrow$ \texttt{R61} & \texttt{Expr\_Minus} $\rightarrow$ 86, \texttt{Expr} $\rightarrow$ 346 \\ \hline
308 & \texttt{;} $\rightarrow$ \texttt{S347} & None \\ \hline
309 & \texttt{;} $\rightarrow$ \texttt{S348} & None \\ \hline
310 & \texttt{-} $\rightarrow$ \texttt{S88}, \texttt{charConst} $\rightarrow$ \texttt{R61}, \texttt{(} $\rightarrow$ \texttt{R61}, \texttt{new} $\rightarrow$ \texttt{R61}, \texttt{number} $\rightarrow$ \texttt{R61}, \texttt{ident} $\rightarrow$ \texttt{R61} & \texttt{Expr\_Minus} $\rightarrow$ 118, \texttt{Condition} $\rightarrow$ 349, \texttt{Expr} $\rightarrow$ 120 \\ \hline
311 & \texttt{-} $\rightarrow$ \texttt{S88}, \texttt{charConst} $\rightarrow$ \texttt{R61}, \texttt{(} $\rightarrow$ \texttt{R61}, \texttt{new} $\rightarrow$ \texttt{R61}, \texttt{number} $\rightarrow$ \texttt{R61}, \texttt{ident} $\rightarrow$ \texttt{R61} & \texttt{Expr\_Minus} $\rightarrow$ 118, \texttt{Condition} $\rightarrow$ 350, \texttt{Expr} $\rightarrow$ 120 \\ \hline
312 & \texttt{ident} $\rightarrow$ \texttt{S122} & \texttt{Designator} $\rightarrow$ 351 \\ \hline
313 & \texttt{-} $\rightarrow$ \texttt{S88}, \texttt{charConst} $\rightarrow$ \texttt{R61}, \texttt{(} $\rightarrow$ \texttt{R61}, \texttt{new} $\rightarrow$ \texttt{R61}, \texttt{number} $\rightarrow$ \texttt{R61}, \texttt{ident} $\rightarrow$ \texttt{R61} & \texttt{Expr\_Minus} $\rightarrow$ 101, \texttt{Expr} $\rightarrow$ 352 \\ \hline
314 & \texttt{;} $\rightarrow$ \texttt{R32}, \texttt{ident} $\rightarrow$ \texttt{R32}, \texttt{while} $\rightarrow$ \texttt{R32}, \texttt{print} $\rightarrow$ \texttt{R32}, \texttt{return} $\rightarrow$ \texttt{R32}, \texttt{if} $\rightarrow$ \texttt{R32}, \texttt{\}} $\rightarrow$ \texttt{R32}, \texttt{read} $\rightarrow$ \texttt{R32}, \texttt{\{} $\rightarrow$ \texttt{R32} & None \\ \hline
315 & \texttt{read} $\rightarrow$ \texttt{S76}, \texttt{print} $\rightarrow$ \texttt{S77}, \texttt{if} $\rightarrow$ \texttt{S78}, \texttt{while} $\rightarrow$ \texttt{S74}, \texttt{\{} $\rightarrow$ \texttt{S68}, \texttt{;} $\rightarrow$ \texttt{S67}, \texttt{return} $\rightarrow$ \texttt{S70}, \texttt{ident} $\rightarrow$ \texttt{S73} & \texttt{Designator} $\rightarrow$ 69, \texttt{Block} $\rightarrow$ 75, \texttt{Statement} $\rightarrow$ 353 \\ \hline
316 & \texttt{,} $\rightarrow$ \texttt{R62}, \texttt{)} $\rightarrow$ \texttt{R62} & None \\ \hline
317 & \texttt{-} $\rightarrow$ \texttt{R67}, \texttt{,} $\rightarrow$ \texttt{R67}, \texttt{)} $\rightarrow$ \texttt{R67}, \texttt{+} $\rightarrow$ \texttt{R67} & None \\ \hline
318 & \texttt{/} $\rightarrow$ \texttt{R82}, \texttt{,} $\rightarrow$ \texttt{R82}, \texttt{\%} $\rightarrow$ \texttt{R82}, \texttt{-} $\rightarrow$ \texttt{R82}, \texttt{)} $\rightarrow$ \texttt{R82}, \texttt{(} $\rightarrow$ \texttt{R82}, \texttt{*} $\rightarrow$ \texttt{R82}, \texttt{+} $\rightarrow$ \texttt{R82} & None \\ \hline
319 & \texttt{)} $\rightarrow$ \texttt{R84}, \texttt{[} $\rightarrow$ \texttt{S194}, \texttt{*} $\rightarrow$ \texttt{R84}, \texttt{.} $\rightarrow$ \texttt{S193}, \texttt{(} $\rightarrow$ \texttt{R84}, \texttt{-} $\rightarrow$ \texttt{R84}, \texttt{,} $\rightarrow$ \texttt{R84}, \texttt{+} $\rightarrow$ \texttt{R84}, \texttt{/} $\rightarrow$ \texttt{R84}, \texttt{\%} $\rightarrow$ \texttt{R84} & \texttt{Designator\_Tail} $\rightarrow$ 354 \\ \hline
320 & \texttt{*} $\rightarrow$ \texttt{R47}, \texttt{+} $\rightarrow$ \texttt{R47}, \texttt{-} $\rightarrow$ \texttt{R47}, \texttt{)} $\rightarrow$ \texttt{R47}, \texttt{\%} $\rightarrow$ \texttt{R47}, \texttt{/} $\rightarrow$ \texttt{R47}, \texttt{,} $\rightarrow$ \texttt{R47} & None \\ \hline
321 & \texttt{]} $\rightarrow$ \texttt{S355} & None \\ \hline
322 & \texttt{-} $\rightarrow$ \texttt{S138}, \texttt{+} $\rightarrow$ \texttt{S137}, \texttt{)} $\rightarrow$ \texttt{R63} & \texttt{Addop} $\rightarrow$ 269, \texttt{Expr\_Tail} $\rightarrow$ 356 \\ \hline
323 & \texttt{)} $\rightarrow$ \texttt{R76}, \texttt{\%} $\rightarrow$ \texttt{R76}, \texttt{/} $\rightarrow$ \texttt{R76}, \texttt{*} $\rightarrow$ \texttt{R76}, \texttt{+} $\rightarrow$ \texttt{R76}, \texttt{-} $\rightarrow$ \texttt{R76} & None \\ \hline
324 & \texttt{*} $\rightarrow$ \texttt{S143}, \texttt{/} $\rightarrow$ \texttt{S144}, \texttt{\%} $\rightarrow$ \texttt{S145}, \texttt{+} $\rightarrow$ \texttt{R68}, \texttt{-} $\rightarrow$ \texttt{R68}, \texttt{)} $\rightarrow$ \texttt{R68} & \texttt{Term\_Tail} $\rightarrow$ 357, \texttt{Mulop} $\rightarrow$ 273 \\ \hline
325 & \texttt{]} $\rightarrow$ \texttt{S358} & None \\ \hline
326 & \texttt{)} $\rightarrow$ \texttt{R84}, \texttt{[} $\rightarrow$ \texttt{S274}, \texttt{.} $\rightarrow$ \texttt{S276}, \texttt{*} $\rightarrow$ \texttt{R84}, \texttt{(} $\rightarrow$ \texttt{R84}, \texttt{+} $\rightarrow$ \texttt{R84}, \texttt{/} $\rightarrow$ \texttt{R84}, \texttt{\%} $\rightarrow$ \texttt{R84}, \texttt{-} $\rightarrow$ \texttt{R84} & \texttt{Designator\_Tail} $\rightarrow$ 359 \\ \hline
327 & \texttt{)} $\rightarrow$ \texttt{S360} & None \\ \hline
328 & \texttt{-} $\rightarrow$ \texttt{S88}, \texttt{charConst} $\rightarrow$ \texttt{R61}, \texttt{(} $\rightarrow$ \texttt{R61}, \texttt{new} $\rightarrow$ \texttt{R61}, \texttt{number} $\rightarrow$ \texttt{R61}, \texttt{ident} $\rightarrow$ \texttt{R61} & \texttt{Expr\_Minus} $\rightarrow$ 115, \texttt{Expr} $\rightarrow$ 361 \\ \hline
329 & \texttt{-} $\rightarrow$ \texttt{R75}, \texttt{)} $\rightarrow$ \texttt{R75}, \texttt{*} $\rightarrow$ \texttt{R75}, \texttt{+} $\rightarrow$ \texttt{R75}, \texttt{/} $\rightarrow$ \texttt{R75}, \texttt{\%} $\rightarrow$ \texttt{R75} & None \\ \hline
330 & \texttt{-} $\rightarrow$ \texttt{R83}, \texttt{\%} $\rightarrow$ \texttt{R83}, \texttt{+} $\rightarrow$ \texttt{R83}, \texttt{;} $\rightarrow$ \texttt{R83}, \texttt{(} $\rightarrow$ \texttt{R83}, \texttt{*} $\rightarrow$ \texttt{R83}, \texttt{/} $\rightarrow$ \texttt{R83} & None \\ \hline
331 & \texttt{-} $\rightarrow$ \texttt{R79}, \texttt{;} $\rightarrow$ \texttt{R79}, \texttt{/} $\rightarrow$ \texttt{R79}, \texttt{\%} $\rightarrow$ \texttt{R79}, \texttt{*} $\rightarrow$ \texttt{R79}, \texttt{+} $\rightarrow$ \texttt{R79} & None \\ \hline
332 & \texttt{]} $\rightarrow$ \texttt{R62} & None \\ \hline
333 & \texttt{-} $\rightarrow$ \texttt{R67}, \texttt{]} $\rightarrow$ \texttt{R67}, \texttt{+} $\rightarrow$ \texttt{R67} & None \\ \hline
334 & \texttt{[} $\rightarrow$ \texttt{S222}, \texttt{.} $\rightarrow$ \texttt{S224}, \texttt{*} $\rightarrow$ \texttt{R84}, \texttt{(} $\rightarrow$ \texttt{R84}, \texttt{-} $\rightarrow$ \texttt{R84}, \texttt{]} $\rightarrow$ \texttt{R84}, \texttt{+} $\rightarrow$ \texttt{R84}, \texttt{/} $\rightarrow$ \texttt{R84}, \texttt{\%} $\rightarrow$ \texttt{R84} & \texttt{Designator\_Tail} $\rightarrow$ 362 \\ \hline
335 & \texttt{/} $\rightarrow$ \texttt{R82}, \texttt{+} $\rightarrow$ \texttt{R82}, \texttt{\%} $\rightarrow$ \texttt{R82}, \texttt{]} $\rightarrow$ \texttt{R82}, \texttt{*} $\rightarrow$ \texttt{R82}, \texttt{-} $\rightarrow$ \texttt{R82}, \texttt{(} $\rightarrow$ \texttt{R82} & None \\ \hline
336 & \texttt{*} $\rightarrow$ \texttt{R47}, \texttt{+} $\rightarrow$ \texttt{R47}, \texttt{]} $\rightarrow$ \texttt{R47}, \texttt{-} $\rightarrow$ \texttt{R47}, \texttt{\%} $\rightarrow$ \texttt{R47}, \texttt{/} $\rightarrow$ \texttt{R47} & None \\ \hline
337 & \texttt{]} $\rightarrow$ \texttt{S363} & None \\ \hline
338 & \texttt{!=} $\rightarrow$ \texttt{R62}, \texttt{>=} $\rightarrow$ \texttt{R62}, \texttt{<} $\rightarrow$ \texttt{R62}, \texttt{>} $\rightarrow$ \texttt{R62}, \texttt{==} $\rightarrow$ \texttt{R62}, \texttt{<=} $\rightarrow$ \texttt{R62} & None \\ \hline
339 & \texttt{<} $\rightarrow$ \texttt{R67}, \texttt{+} $\rightarrow$ \texttt{R67}, \texttt{<=} $\rightarrow$ \texttt{R67}, \texttt{!=} $\rightarrow$ \texttt{R67}, \texttt{-} $\rightarrow$ \texttt{R67}, \texttt{>=} $\rightarrow$ \texttt{R67}, \texttt{>} $\rightarrow$ \texttt{R67}, \texttt{==} $\rightarrow$ \texttt{R67} & None \\ \hline
340 & \texttt{/} $\rightarrow$ \texttt{R82}, \texttt{<=} $\rightarrow$ \texttt{R82}, \texttt{!=} $\rightarrow$ \texttt{R82}, \texttt{\%} $\rightarrow$ \texttt{R82}, \texttt{>=} $\rightarrow$ \texttt{R82}, \texttt{-} $\rightarrow$ \texttt{R82}, \texttt{(} $\rightarrow$ \texttt{R82}, \texttt{>} $\rightarrow$ \texttt{R82}, \texttt{==} $\rightarrow$ \texttt{R82}, \texttt{*} $\rightarrow$ \texttt{R82}, \texttt{+} $\rightarrow$ \texttt{R82}, \texttt{<} $\rightarrow$ \texttt{R82} & None \\ \hline
341 & \texttt{[} $\rightarrow$ \texttt{S236}, \texttt{*} $\rightarrow$ \texttt{R84}, \texttt{.} $\rightarrow$ \texttt{S235}, \texttt{<=} $\rightarrow$ \texttt{R84}, \texttt{>=} $\rightarrow$ \texttt{R84}, \texttt{(} $\rightarrow$ \texttt{R84}, \texttt{==} $\rightarrow$ \texttt{R84}, \texttt{-} $\rightarrow$ \texttt{R84}, \texttt{>} $\rightarrow$ \texttt{R84}, \texttt{<} $\rightarrow$ \texttt{R84}, \texttt{+} $\rightarrow$ \texttt{R84}, \texttt{/} $\rightarrow$ \texttt{R84}, \texttt{!=} $\rightarrow$ \texttt{R84}, \texttt{\%} $\rightarrow$ \texttt{R84} & \texttt{Designator\_Tail} $\rightarrow$ 364 \\ \hline
342 & \texttt{-} $\rightarrow$ \texttt{R47}, \texttt{!=} $\rightarrow$ \texttt{R47}, \texttt{>} $\rightarrow$ \texttt{R47}, \texttt{==} $\rightarrow$ \texttt{R47}, \texttt{<=} $\rightarrow$ \texttt{R47}, \texttt{*} $\rightarrow$ \texttt{R47}, \texttt{+} $\rightarrow$ \texttt{R47}, \texttt{<} $\rightarrow$ \texttt{R47}, \texttt{\%} $\rightarrow$ \texttt{R47}, \texttt{/} $\rightarrow$ \texttt{R47}, \texttt{>=} $\rightarrow$ \texttt{R47} & None \\ \hline
343 & \texttt{]} $\rightarrow$ \texttt{S365} & None \\ \hline
344 & \texttt{)} $\rightarrow$ \texttt{R83} & None \\ \hline
345 & \texttt{\{} $\rightarrow$ \texttt{R28}, \texttt{else} $\rightarrow$ \texttt{R28}, \texttt{;} $\rightarrow$ \texttt{R28}, \texttt{ident} $\rightarrow$ \texttt{R28}, \texttt{while} $\rightarrow$ \texttt{R28}, \texttt{print} $\rightarrow$ \texttt{R28}, \texttt{return} $\rightarrow$ \texttt{R28}, \texttt{if} $\rightarrow$ \texttt{R28}, \texttt{\}} $\rightarrow$ \texttt{R28}, \texttt{read} $\rightarrow$ \texttt{R28} & None \\ \hline
346 & \texttt{;} $\rightarrow$ \texttt{S366} & None \\ \hline
347 & \texttt{if} $\rightarrow$ \texttt{R40}, \texttt{print} $\rightarrow$ \texttt{R40}, \texttt{\}} $\rightarrow$ \texttt{R40}, \texttt{read} $\rightarrow$ \texttt{R40}, \texttt{\{} $\rightarrow$ \texttt{R40}, \texttt{else} $\rightarrow$ \texttt{R40}, \texttt{ident} $\rightarrow$ \texttt{R40}, \texttt{while} $\rightarrow$ \texttt{R40}, \texttt{;} $\rightarrow$ \texttt{R40}, \texttt{return} $\rightarrow$ \texttt{R40} & None \\ \hline
348 & \texttt{else} $\rightarrow$ \texttt{R34}, \texttt{print} $\rightarrow$ \texttt{R34}, \texttt{return} $\rightarrow$ \texttt{R34}, \texttt{\}} $\rightarrow$ \texttt{R34}, \texttt{if} $\rightarrow$ \texttt{R34}, \texttt{read} $\rightarrow$ \texttt{R34}, \texttt{ident} $\rightarrow$ \texttt{R34}, \texttt{\{} $\rightarrow$ \texttt{R34}, \texttt{;} $\rightarrow$ \texttt{R34}, \texttt{while} $\rightarrow$ \texttt{R34} & None \\ \hline
349 & \texttt{)} $\rightarrow$ \texttt{S367} & None \\ \hline
350 & \texttt{)} $\rightarrow$ \texttt{S368} & None \\ \hline
351 & \texttt{)} $\rightarrow$ \texttt{S369} & None \\ \hline
352 & \texttt{,} $\rightarrow$ \texttt{S185}, \texttt{)} $\rightarrow$ \texttt{R46} & \texttt{Print\_Opt} $\rightarrow$ 370 \\ \hline
353 & \texttt{\{} $\rightarrow$ \texttt{R41}, \texttt{ident} $\rightarrow$ \texttt{R41}, \texttt{;} $\rightarrow$ \texttt{R41}, \texttt{while} $\rightarrow$ \texttt{R41}, \texttt{print} $\rightarrow$ \texttt{R41}, \texttt{\}} $\rightarrow$ \texttt{R41}, \texttt{return} $\rightarrow$ \texttt{R41}, \texttt{if} $\rightarrow$ \texttt{R41}, \texttt{read} $\rightarrow$ \texttt{R41} & None \\ \hline
354 & \texttt{,} $\rightarrow$ \texttt{R83}, \texttt{\%} $\rightarrow$ \texttt{R83}, \texttt{)} $\rightarrow$ \texttt{R83}, \texttt{(} $\rightarrow$ \texttt{R83}, \texttt{-} $\rightarrow$ \texttt{R83}, \texttt{*} $\rightarrow$ \texttt{R83}, \texttt{+} $\rightarrow$ \texttt{R83}, \texttt{/} $\rightarrow$ \texttt{R83} & None \\ \hline
355 & \texttt{-} $\rightarrow$ \texttt{R79}, \texttt{)} $\rightarrow$ \texttt{R79}, \texttt{/} $\rightarrow$ \texttt{R79}, \texttt{\%} $\rightarrow$ \texttt{R79}, \texttt{,} $\rightarrow$ \texttt{R79}, \texttt{*} $\rightarrow$ \texttt{R79}, \texttt{+} $\rightarrow$ \texttt{R79} & None \\ \hline
356 & \texttt{)} $\rightarrow$ \texttt{R62} & None \\ \hline
357 & \texttt{-} $\rightarrow$ \texttt{R67}, \texttt{)} $\rightarrow$ \texttt{R67}, \texttt{+} $\rightarrow$ \texttt{R67} & None \\ \hline
358 & \texttt{)} $\rightarrow$ \texttt{R84}, \texttt{[} $\rightarrow$ \texttt{S274}, \texttt{.} $\rightarrow$ \texttt{S276}, \texttt{*} $\rightarrow$ \texttt{R84}, \texttt{(} $\rightarrow$ \texttt{R84}, \texttt{-} $\rightarrow$ \texttt{R84}, \texttt{+} $\rightarrow$ \texttt{R84}, \texttt{/} $\rightarrow$ \texttt{R84}, \texttt{\%} $\rightarrow$ \texttt{R84} & \texttt{Designator\_Tail} $\rightarrow$ 371 \\ \hline
359 & \texttt{/} $\rightarrow$ \texttt{R82}, \texttt{\%} $\rightarrow$ \texttt{R82}, \texttt{+} $\rightarrow$ \texttt{R82}, \texttt{*} $\rightarrow$ \texttt{R82}, \texttt{-} $\rightarrow$ \texttt{R82}, \texttt{)} $\rightarrow$ \texttt{R82}, \texttt{(} $\rightarrow$ \texttt{R82} & None \\ \hline
360 & \texttt{*} $\rightarrow$ \texttt{R47}, \texttt{+} $\rightarrow$ \texttt{R47}, \texttt{-} $\rightarrow$ \texttt{R47}, \texttt{)} $\rightarrow$ \texttt{R47}, \texttt{\%} $\rightarrow$ \texttt{R47}, \texttt{/} $\rightarrow$ \texttt{R47} & None \\ \hline
361 & \texttt{]} $\rightarrow$ \texttt{S372} & None \\ \hline
362 & \texttt{-} $\rightarrow$ \texttt{R83}, \texttt{\%} $\rightarrow$ \texttt{R83}, \texttt{+} $\rightarrow$ \texttt{R83}, \texttt{*} $\rightarrow$ \texttt{R83}, \texttt{(} $\rightarrow$ \texttt{R83}, \texttt{]} $\rightarrow$ \texttt{R83}, \texttt{/} $\rightarrow$ \texttt{R83} & None \\ \hline
363 & \texttt{-} $\rightarrow$ \texttt{R79}, \texttt{/} $\rightarrow$ \texttt{R79}, \texttt{\%} $\rightarrow$ \texttt{R79}, \texttt{*} $\rightarrow$ \texttt{R79}, \texttt{+} $\rightarrow$ \texttt{R79}, \texttt{]} $\rightarrow$ \texttt{R79} & None \\ \hline
364 & \texttt{<} $\rightarrow$ \texttt{R83}, \texttt{\%} $\rightarrow$ \texttt{R83}, \texttt{<=} $\rightarrow$ \texttt{R83}, \texttt{>=} $\rightarrow$ \texttt{R83}, \texttt{!=} $\rightarrow$ \texttt{R83}, \texttt{(} $\rightarrow$ \texttt{R83}, \texttt{-} $\rightarrow$ \texttt{R83}, \texttt{>} $\rightarrow$ \texttt{R83}, \texttt{==} $\rightarrow$ \texttt{R83}, \texttt{*} $\rightarrow$ \texttt{R83}, \texttt{+} $\rightarrow$ \texttt{R83}, \texttt{/} $\rightarrow$ \texttt{R83} & None \\ \hline
365 & \texttt{<} $\rightarrow$ \texttt{R79}, \texttt{/} $\rightarrow$ \texttt{R79}, \texttt{<=} $\rightarrow$ \texttt{R79}, \texttt{\%} $\rightarrow$ \texttt{R79}, \texttt{!=} $\rightarrow$ \texttt{R79}, \texttt{>=} $\rightarrow$ \texttt{R79}, \texttt{-} $\rightarrow$ \texttt{R79}, \texttt{>} $\rightarrow$ \texttt{R79}, \texttt{==} $\rightarrow$ \texttt{R79}, \texttt{*} $\rightarrow$ \texttt{R79}, \texttt{+} $\rightarrow$ \texttt{R79} & None \\ \hline
366 & \texttt{print} $\rightarrow$ \texttt{R39}, \texttt{if} $\rightarrow$ \texttt{R39}, \texttt{read} $\rightarrow$ \texttt{R39}, \texttt{\{} $\rightarrow$ \texttt{R39}, \texttt{ident} $\rightarrow$ \texttt{R39}, \texttt{while} $\rightarrow$ \texttt{R39}, \texttt{;} $\rightarrow$ \texttt{R39}, \texttt{else} $\rightarrow$ \texttt{R39}, \texttt{\}} $\rightarrow$ \texttt{R39}, \texttt{return} $\rightarrow$ \texttt{R39} & None \\ \hline
367 & \texttt{read} $\rightarrow$ \texttt{S256}, \texttt{print} $\rightarrow$ \texttt{S257}, \texttt{if} $\rightarrow$ \texttt{S253}, \texttt{while} $\rightarrow$ \texttt{S254}, \texttt{\{} $\rightarrow$ \texttt{S250}, \texttt{;} $\rightarrow$ \texttt{S249}, \texttt{return} $\rightarrow$ \texttt{S252}, \texttt{ident} $\rightarrow$ \texttt{S73} & \texttt{Designator} $\rightarrow$ 251, \texttt{Block} $\rightarrow$ 255, \texttt{Statement} $\rightarrow$ 373 \\ \hline
368 & \texttt{read} $\rightarrow$ \texttt{S256}, \texttt{print} $\rightarrow$ \texttt{S257}, \texttt{if} $\rightarrow$ \texttt{S253}, \texttt{while} $\rightarrow$ \texttt{S254}, \texttt{\{} $\rightarrow$ \texttt{S250}, \texttt{;} $\rightarrow$ \texttt{S249}, \texttt{return} $\rightarrow$ \texttt{S252}, \texttt{ident} $\rightarrow$ \texttt{S73} & \texttt{Designator} $\rightarrow$ 251, \texttt{Block} $\rightarrow$ 255, \texttt{Statement} $\rightarrow$ 374 \\ \hline
369 & \texttt{;} $\rightarrow$ \texttt{S375} & None \\ \hline
370 & \texttt{)} $\rightarrow$ \texttt{S376} & None \\ \hline
371 & \texttt{-} $\rightarrow$ \texttt{R83}, \texttt{\%} $\rightarrow$ \texttt{R83}, \texttt{+} $\rightarrow$ \texttt{R83}, \texttt{)} $\rightarrow$ \texttt{R83}, \texttt{(} $\rightarrow$ \texttt{R83}, \texttt{*} $\rightarrow$ \texttt{R83}, \texttt{/} $\rightarrow$ \texttt{R83} & None \\ \hline
372 & \texttt{-} $\rightarrow$ \texttt{R79}, \texttt{)} $\rightarrow$ \texttt{R79}, \texttt{/} $\rightarrow$ \texttt{R79}, \texttt{\%} $\rightarrow$ \texttt{R79}, \texttt{*} $\rightarrow$ \texttt{R79}, \texttt{+} $\rightarrow$ \texttt{R79} & None \\ \hline
373 & \texttt{return} $\rightarrow$ \texttt{R42}, \texttt{else} $\rightarrow$ \texttt{S378}, \texttt{if} $\rightarrow$ \texttt{R42}, \texttt{\}} $\rightarrow$ \texttt{R42}, \texttt{read} $\rightarrow$ \texttt{R42}, \texttt{\{} $\rightarrow$ \texttt{R42}, \texttt{ident} $\rightarrow$ \texttt{R42}, \texttt{;} $\rightarrow$ \texttt{R42}, \texttt{while} $\rightarrow$ \texttt{R42}, \texttt{print} $\rightarrow$ \texttt{R42} & \texttt{Else\_Opt} $\rightarrow$ 377 \\ \hline
374 & \texttt{return} $\rightarrow$ \texttt{R33}, \texttt{if} $\rightarrow$ \texttt{R33}, \texttt{print} $\rightarrow$ \texttt{R33}, \texttt{\}} $\rightarrow$ \texttt{R33}, \texttt{;} $\rightarrow$ \texttt{R33}, \texttt{read} $\rightarrow$ \texttt{R33}, \texttt{\{} $\rightarrow$ \texttt{R33}, \texttt{ident} $\rightarrow$ \texttt{R33}, \texttt{while} $\rightarrow$ \texttt{R33}, \texttt{else} $\rightarrow$ \texttt{R33} & None \\ \hline
375 & \texttt{read} $\rightarrow$ \texttt{R35}, \texttt{\{} $\rightarrow$ \texttt{R35}, \texttt{while} $\rightarrow$ \texttt{R35}, \texttt{else} $\rightarrow$ \texttt{R35}, \texttt{;} $\rightarrow$ \texttt{R35}, \texttt{ident} $\rightarrow$ \texttt{R35}, \texttt{print} $\rightarrow$ \texttt{R35}, \texttt{return} $\rightarrow$ \texttt{R35}, \texttt{if} $\rightarrow$ \texttt{R35}, \texttt{\}} $\rightarrow$ \texttt{R35} & None \\ \hline
376 & \texttt{;} $\rightarrow$ \texttt{S379} & None \\ \hline
377 & \texttt{else} $\rightarrow$ \texttt{R32}, \texttt{ident} $\rightarrow$ \texttt{R32}, \texttt{while} $\rightarrow$ \texttt{R32}, \texttt{;} $\rightarrow$ \texttt{R32}, \texttt{print} $\rightarrow$ \texttt{R32}, \texttt{return} $\rightarrow$ \texttt{R32}, \texttt{if} $\rightarrow$ \texttt{R32}, \texttt{\}} $\rightarrow$ \texttt{R32}, \texttt{read} $\rightarrow$ \texttt{R32}, \texttt{\{} $\rightarrow$ \texttt{R32} & None \\ \hline
378 & \texttt{read} $\rightarrow$ \texttt{S256}, \texttt{print} $\rightarrow$ \texttt{S257}, \texttt{if} $\rightarrow$ \texttt{S253}, \texttt{while} $\rightarrow$ \texttt{S254}, \texttt{\{} $\rightarrow$ \texttt{S250}, \texttt{;} $\rightarrow$ \texttt{S249}, \texttt{return} $\rightarrow$ \texttt{S252}, \texttt{ident} $\rightarrow$ \texttt{S73} & \texttt{Designator} $\rightarrow$ 251, \texttt{Block} $\rightarrow$ 255, \texttt{Statement} $\rightarrow$ 380 \\ \hline
379 & \texttt{read} $\rightarrow$ \texttt{R36}, \texttt{\{} $\rightarrow$ \texttt{R36}, \texttt{ident} $\rightarrow$ \texttt{R36}, \texttt{;} $\rightarrow$ \texttt{R36}, \texttt{while} $\rightarrow$ \texttt{R36}, \texttt{else} $\rightarrow$ \texttt{R36}, \texttt{print} $\rightarrow$ \texttt{R36}, \texttt{return} $\rightarrow$ \texttt{R36}, \texttt{\}} $\rightarrow$ \texttt{R36}, \texttt{if} $\rightarrow$ \texttt{R36} & None \\ \hline
380 & \texttt{\{} $\rightarrow$ \texttt{R41}, \texttt{ident} $\rightarrow$ \texttt{R41}, \texttt{;} $\rightarrow$ \texttt{R41}, \texttt{while} $\rightarrow$ \texttt{R41}, \texttt{else} $\rightarrow$ \texttt{R41}, \texttt{print} $\rightarrow$ \texttt{R41}, \texttt{\}} $\rightarrow$ \texttt{R41}, \texttt{return} $\rightarrow$ \texttt{R41}, \texttt{if} $\rightarrow$ \texttt{R41}, \texttt{read} $\rightarrow$ \texttt{R41} & None \\ \hline
\end{longtable}

\subsection{Trace Segment for Declaration Statement: \texttt{int x;}}
Below is a step-by-step trace showing the stack operations during the parsing of \texttt{int x;}:
\begin{enumerate} 
    \item \textbf{State 0}: Top of state stack is `0`. The current lookahead token is identifier `int`.
    \item \textbf{Shift action}: The parser shifts `int` and transitions to **State 10**.
    \item \textbf{State 10}: Top of stack is `10`. The current lookahead token is identifier `x`.
    \item \textbf{Reduction}: The parser reduces `int` to type symbol $Type$ using rule:
      $$Type \rightarrow \text{ident}$$
      It pops one state (State 10) off the stack. The top state is now `0`. It checks GOTO table entry $\text{Goto}[0, Type] = 8$ and pushes **State 8**.
    \item \textbf{State 8}: Top of stack is `8`. Lookahead token is `x`.
    \item \textbf{Shift action}: Shift identifier `x` and transition to **State 14**.
    \item \textbf{State 14}: Top of stack is `14`. Lookahead token is `;`.
    \item \textbf{Shift action}: Shift punctuation `;` and transition to **State 25**.
    \item \textbf{State 25}: Reduce by rule $VarDecl \rightarrow Type \, \text{ident} \, VarDecl\_Tail \, ;$. 
\end{enumerate}

\newpage

\section{Unified End-to-End Multiphase Execution Trace}
This section displays the exact, raw compiler validation outputs for the \texttt{SimpleSum} program, demonstrating the integration of all five phases:

\subsection{Example MicroJava Source Program}
Below is the complete MicroJava program (\texttt{SimpleSum.mj}) used for generating the execution traces:
\begin{lstlisting}[language=Java, caption=Example MicroJava Program (SimpleSum)]
program SimpleSum
  int x;
  int y;
  int sum;
{
  void main() {
    x = 5;
    y = 10;
    sum = x + y;
    print(sum);
  }
}
\end{lstlisting}

\subsection{Phase 1: Lexical Analyzer Output Stream}
\begin{verbatim}
+----------------------+----------------------------+---------+---------+
| Token Type           | Lexeme                     | Line    | Column  |
+----------------------+----------------------------+---------+---------+
| KW_PROGRAM           | program                    | 1       | 1       |
| IDENTIFIER           | SimpleSum                  | 1       | 9       |
| IDENTIFIER           | int                        | 3       | 3       |
| IDENTIFIER           | x                          | 3       | 7       |
| SEMICOLON            | ;                          | 3       | 8       |
| IDENTIFIER           | int                        | 4       | 3       |
| IDENTIFIER           | y                          | 4       | 7       |
| SEMICOLON            | ;                          | 4       | 8       |
| IDENTIFIER           | int                        | 5       | 3       |
| IDENTIFIER           | sum                        | 5       | 7       |
| SEMICOLON            | ;                          | 5       | 10      |
| LBRACE               | {                          | 6       | 1       |
| KW_VOID              | void                       | 7       | 3       |
| IDENTIFIER           | main                       | 7       | 8       |
| LPAREN               | (                          | 7       | 12      |
| RPAREN               | )                          | 7       | 13      |
| LBRACE               | {                          | 7       | 15      |
| IDENTIFIER           | x                          | 8       | 5       |
| ASSIGN               | =                          | 8       | 7       |
| NUMBER               | 5                          | 8       | 9       |
| SEMICOLON            | ;                          | 8       | 10      |
| IDENTIFIER           | y                          | 9       | 5       |
| ASSIGN               | =                          | 9       | 7       |
| NUMBER               | 10                         | 9       | 9       |
| SEMICOLON            | ;                          | 9       | 11      |
| IDENTIFIER           | sum                        | 10      | 5       |
| ASSIGN               | =                          | 10      | 9       |
| IDENTIFIER           | x                          | 10      | 11      |
| PLUS                 | +                          | 10      | 13      |
| IDENTIFIER           | y                          | 10      | 15      |
| SEMICOLON            | ;                          | 10      | 16      |
| KW_PRINT             | print                      | 11      | 5       |
| LPAREN               | (                          | 11      | 10      |
| IDENTIFIER           | sum                        | 11      | 11      |
| RPAREN               | )                          | 11      | 14      |
| SEMICOLON            | ;                          | 11      | 15      |
| RBRACE               | }                          | 12      | 3       |
| RBRACE               | }                          | 13      | 1       |
| EOF                  | EOF                        | 14      | 1       |
+----------------------+----------------------------+---------+---------+
[SUCCESS] Lexical scan completed with 0 lexical errors. Total tokens: 39
\end{verbatim}

\subsection{Phase 2: Recursive Descent AST / Parse Tree}
\begin{verbatim}
├── Program (token: "program")
│  ├── KW_PROGRAM (token: "program")
│  ├── IDENTIFIER (token: "SimpleSum")
│  ├── VarDecl (token: "int")
│  │  ├── Type (token: "int")
│  │  │  ├── IDENTIFIER (token: "int")
│  │  ├── IDENTIFIER (token: "x")
│  │  ├── SEMICOLON (token: ";")
│  ├── VarDecl (token: "int")
│  │  ├── Type (token: "int")
│  │  │  ├── IDENTIFIER (token: "int")
│  │  ├── IDENTIFIER (token: "y")
│  │  ├── SEMICOLON (token: ";")
│  ├── VarDecl (token: "int")
│  │  ├── Type (token: "int")
│  │  │  ├── IDENTIFIER (token: "int")
│  │  ├── IDENTIFIER (token: "sum")
│  │  ├── SEMICOLON (token: ";")
│  ├── LBRACE (token: "{")
│  ├── MethodDecl (token: "void")
│  │  ├── KW_VOID (token: "void")
│  │  ├── IDENTIFIER (token: "main")
│  │  ├── LPAREN (token: "(")
│  │  ├── RPAREN (token: ")")
│  │  ├── Block (token: "{")
│  │  │  ├── LBRACE (token: "{")
│  │  │  ├── Statement (token: "x")
│  │  │  │  ├── Designator (token: "x")
│  │  │  │  │  ├── IDENTIFIER (token: "x")
│  │  │  │  ├── ASSIGN (token: "=")
│  │  │  │  ├── Expr (token: "5")
│  │  │  │  │  ├── Term (token: "5")
│  │  │  │  │  │  ├── Factor (token: "5")
│  │  │  │  │  │  │  ├── NUMBER (token: "5")
│  │  │  │  ├── SEMICOLON (token: ";")
│  │  │  ├── Statement (token: "y")
│  │  │  │  ├── Designator (token: "y")
│  │  │  │  │  ├── IDENTIFIER (token: "y")
│  │  │  │  ├── ASSIGN (token: "=")
│  │  │  │  ├── Expr (token: "10")
│  │  │  │  │  ├── Term (token: "10")
│  │  │  │  │  │  ├── Factor (token: "10")
│  │  │  │  │  │  │  ├── NUMBER (token: "10")
│  │  │  │  ├── SEMICOLON (token: ";")
│  │  │  ├── Statement (token: "sum")
│  │  │  │  ├── Designator (token: "sum")
│  │  │  │  │  ├── IDENTIFIER (token: "sum")
│  │  │  │  ├── ASSIGN (token: "=")
│  │  │  │  ├── Expr (token: "x")
│  │  │  │  │  ├── Term (token: "x")
│  │  │  │  │  │  ├── Factor (token: "x")
│  │  │  │  │  │  │  ├── Designator (token: "x")
│  │  │  │  │  │  │  │  ├── IDENTIFIER (token: "x")
│  │  │  │  │  ├── Addop (token: "+")
│  │  │  │  │  │  ├── PLUS (token: "+")
│  │  │  │  │  ├── Term (token: "y")
│  │  │  │  │  │  ├── Factor (token: "y")
│  │  │  │  │  │  │  ├── Designator (token: "y")
│  │  │  │  │  │  │  │  ├── IDENTIFIER (token: "y")
│  │  │  │  ├── SEMICOLON (token: ";")
│  │  │  ├── Statement (token: "print")
│  │  │  │  ├── KW_PRINT (token: "print")
│  │  │  │  ├── LPAREN (token: "(")
│  │  │  │  ├── Expr (token: "sum")
│  │  │  │  │  ├── Term (token: "sum")
│  │  │  │  │  │  ├── Factor (token: "sum")
│  │  │  │  │  │  │  ├── Designator (token: "sum")
│  │  │  │  │  │  │  │  ├── IDENTIFIER (token: "sum")
│  │  │  │  ├── RPAREN (token: ")")
│  │  │  │  ├── SEMICOLON (token: ";")
│  │  │  ├── RBRACE (token: "}")
│  ├── RBRACE (token: "}")
------------------------------------------------------------------------------
[SUCCESS] Recursive Descent Parsing completed with 0 errors.
\end{verbatim}

\subsection{Phase 3: Symbol Table Registry}
\begin{verbatim}
+-------+----------------------+------------+----------------------------+------+
| Scope | Symbol Name          | Kind       | Data Type                  | Line |
+-------+----------------------+------------+----------------------------+------+
| 1     | main                 | METHOD     | void                       | 7    |
| 1     | sum                  | VAR        | int                        | 5    |
| 1     | y                    | VAR        | int                        | 4    |
| 1     | x                    | VAR        | int                        | 3    |
| 0     | SimpleSum            | CLASS      | void                       | 1    |
| 0     | len                  | METHOD     | int                        | 0    |
| 0     | ord                  | METHOD     | int                        | 0    |
| 0     | chr                  | METHOD     | char                       | 0    |
+-------+----------------------+------------+----------------------------+------+
\end{verbatim}

\subsection{Phase 4: LL(1) Parsing Rules (Actions Only)}
\begin{verbatim}
Applied Rule Program -> program ident Program_Body { MethodDecls }
Match token 'program'
Match token 'ident'
Applied Rule Program_Body -> VarDecl Program_Body
Applied Rule VarDecl -> Type ident VarDecl_Tail ;
Applied Rule Type -> ident Type_Opt
Match token 'ident'
Applied Rule Type_Opt -> epsilon
Match token 'ident'
Applied Rule VarDecl_Tail -> epsilon
Match token ';'
Applied Rule Program_Body -> VarDecl Program_Body
Applied Rule VarDecl -> Type ident VarDecl_Tail ;
Applied Rule Type -> ident Type_Opt
Match token 'ident'
Applied Rule Type_Opt -> epsilon
Match token 'ident'
Applied Rule VarDecl_Tail -> epsilon
Match token ';'
Applied Rule Program_Body -> VarDecl Program_Body
Applied Rule VarDecl -> Type ident VarDecl_Tail ;
Applied Rule Type -> ident Type_Opt
Match token 'ident'
Applied Rule Type_Opt -> epsilon
Match token 'ident'
Applied Rule VarDecl_Tail -> epsilon
Match token ';'
Applied Rule Program_Body -> epsilon
Match token '{'
Applied Rule MethodDecls -> MethodDecl MethodDecls
Applied Rule MethodDecl -> MethodType ident ( FormPars_Opt ) VarDecls Block
Applied Rule MethodType -> void
Match token 'void'
Match token 'ident'
Match token '('
Applied Rule FormPars_Opt -> epsilon
Match token ')'
Applied Rule VarDecls -> epsilon
Applied Rule Block -> { Statements }
Match token '{'
Applied Rule Statements -> Statement Statements
Applied Rule Statement -> Designator Statement_AssignOrCall
Applied Rule Designator -> ident Designator_Tail
Match token 'ident'
Applied Rule Designator_Tail -> epsilon
Applied Rule Statement_AssignOrCall -> = Expr ;
Match token '='
Applied Rule Expr -> Expr_Minus Term Expr_Tail
Applied Rule Expr_Minus -> epsilon
Applied Rule Term -> Factor Term_Tail
Applied Rule Factor -> number
Match token 'number'
Applied Rule Term_Tail -> epsilon
Applied Rule Expr_Tail -> epsilon
Match token ';'
Applied Rule Statements -> Statement Statements
Applied Rule Statement -> Designator Statement_AssignOrCall
Applied Rule Designator -> ident Designator_Tail
Match token 'ident'
Applied Rule Designator_Tail -> epsilon
Applied Rule Statement_AssignOrCall -> = Expr ;
Match token '='
Applied Rule Expr -> Expr_Minus Term Expr_Tail
Applied Rule Expr_Minus -> epsilon
Applied Rule Term -> Factor Term_Tail
Applied Rule Factor -> number
Match token 'number'
Applied Rule Term_Tail -> epsilon
Applied Rule Expr_Tail -> epsilon
Match token ';'
Applied Rule Statements -> Statement Statements
Applied Rule Statement -> Designator Statement_AssignOrCall
Applied Rule Designator -> ident Designator_Tail
Match token 'ident'
Applied Rule Designator_Tail -> epsilon
Applied Rule Statement_AssignOrCall -> = Expr ;
Match token '='
Applied Rule Expr -> Expr_Minus Term Expr_Tail
Applied Rule Expr_Minus -> epsilon
Applied Rule Term -> Factor Term_Tail
Applied Rule Factor -> Designator Factor_Designator
Applied Rule Designator -> ident Designator_Tail
Match token 'ident'
Applied Rule Designator_Tail -> epsilon
Applied Rule Factor_Designator -> epsilon
Applied Rule Term_Tail -> epsilon
Applied Rule Expr_Tail -> Addop Term Expr_Tail
Applied Rule Addop -> +
Match token '+'
Applied Rule Term -> Factor Term_Tail
Applied Rule Factor -> Designator Factor_Designator
Applied Rule Designator -> ident Designator_Tail
Match token 'ident'
Applied Rule Designator_Tail -> epsilon
Applied Rule Factor_Designator -> epsilon
Applied Rule Term_Tail -> epsilon
Applied Rule Expr_Tail -> epsilon
Match token ';'
Applied Rule Statements -> Statement Statements
Applied Rule Statement -> print ( Expr Print_Opt ) ;
Match token 'print'
Match token '('
Applied Rule Expr -> Expr_Minus Term Expr_Tail
Applied Rule Expr_Minus -> epsilon
Applied Rule Term -> Factor Term_Tail
Applied Rule Factor -> Designator Factor_Designator
Applied Rule Designator -> ident Designator_Tail
Match token 'ident'
Applied Rule Designator_Tail -> epsilon
Applied Rule Factor_Designator -> epsilon
Applied Rule Term_Tail -> epsilon
Applied Rule Expr_Tail -> epsilon
Applied Rule Print_Opt -> epsilon
Match token ')'
Match token ';'
Applied Rule Statements -> epsilon
Match token '}'
Applied Rule MethodDecls -> epsilon
Match token '}'
Match token '$'
------------------------------------------------------------------------------
[SUCCESS] LL(1) Parser completed with 0 errors.
\end{verbatim}

\subsection{Phase 5: Canonical LR(1) Actions (Actions Only)}
\begin{verbatim}
Shift 1
Shift 3
Shift 6
Reduce (27) Type_Opt. Pop 0 states. Push GOTO(6, Type_Opt) = 14.
Reduce (25) Type. Pop 2 states. Push GOTO(3, Type) = 8.
Shift 17
Reduce (11) VarDecl_Tail. Pop 0 states. Push GOTO(17, VarDecl_Tail) = 27.
Shift 34
Reduce (9) VarDecl. Pop 4 states. Push GOTO(3, VarDecl) = 7.
Shift 6
Reduce (27) Type_Opt. Pop 0 states. Push GOTO(6, Type_Opt) = 14.
Reduce (25) Type. Pop 2 states. Push GOTO(7, Type) = 8.
Shift 17
Reduce (11) VarDecl_Tail. Pop 0 states. Push GOTO(17, VarDecl_Tail) = 27.
Shift 34
Reduce (9) VarDecl. Pop 4 states. Push GOTO(7, VarDecl) = 7.
Shift 6
Reduce (27) Type_Opt. Pop 0 states. Push GOTO(6, Type_Opt) = 14.
Reduce (25) Type. Pop 2 states. Push GOTO(7, Type) = 8.
Shift 17
Reduce (11) VarDecl_Tail. Pop 0 states. Push GOTO(17, VarDecl_Tail) = 27.
Shift 34
Reduce (9) VarDecl. Pop 4 states. Push GOTO(7, VarDecl) = 7.
Reduce (5) Program_Body. Pop 0 states. Push GOTO(7, Program_Body) = 16.
Reduce (3) Program_Body. Pop 2 states. Push GOTO(7, Program_Body) = 16.
Reduce (3) Program_Body. Pop 2 states. Push GOTO(7, Program_Body) = 16.
Reduce (3) Program_Body. Pop 2 states. Push GOTO(3, Program_Body) = 5.
Shift 13
Shift 21
Reduce (19) MethodType. Pop 1 state. Push GOTO(13, MethodType) = 24.
Shift 32
Shift 40
Reduce (21) FormPars_Opt. Pop 0 states. Push GOTO(40, FormPars_Opt) = 48.
Shift 53
Reduce (14) VarDecls. Pop 0 states. Push GOTO(53, VarDecls) = 58.
Shift 64
Shift 73
Reduce (84) Designator_Tail. Pop 0 states. Push GOTO(73, Designator_Tail) = 93.
Reduce (81) Designator. Pop 2 states. Push GOTO(64, Designator) = 69.
Shift 84
Reduce (61) Expr_Minus. Pop 0 states. Push GOTO(84, Expr_Minus) = 86.
Shift 107
Reduce (73) Factor. Pop 1 state. Push GOTO(86, Factor) = 110.
Reduce (68) Term_Tail. Pop 0 states. Push GOTO(110, Term_Tail) = 146.
Reduce (66) Term. Pop 2 states. Push GOTO(86, Term) = 106.
Reduce (63) Expr_Tail. Pop 0 states. Push GOTO(106, Expr_Tail) = 140.
Reduce (59) Expr. Pop 3 states. Push GOTO(84, Expr) = 104.
Shift 136
Reduce (39) Statement_AssignOrCall. Pop 3 states. Push GOTO(69, Statement_AssignOrCall) = 82.
Reduce (31) Statement. Pop 2 states. Push GOTO(64, Statement) = 72.
Shift 73
Reduce (84) Designator_Tail. Pop 0 states. Push GOTO(73, Designator_Tail) = 93.
Reduce (81) Designator. Pop 2 states. Push GOTO(72, Designator) = 69.
Shift 84
Reduce (61) Expr_Minus. Pop 0 states. Push GOTO(84, Expr_Minus) = 86.
Shift 107
Reduce (73) Factor. Pop 1 state. Push GOTO(86, Factor) = 110.
Reduce (68) Term_Tail. Pop 0 states. Push GOTO(110, Term_Tail) = 146.
Reduce (66) Term. Pop 2 states. Push GOTO(86, Term) = 106.
Reduce (63) Expr_Tail. Pop 0 states. Push GOTO(106, Expr_Tail) = 140.
Reduce (59) Expr. Pop 3 states. Push GOTO(84, Expr) = 104.
Shift 136
Reduce (39) Statement_AssignOrCall. Pop 3 states. Push GOTO(69, Statement_AssignOrCall) = 82.
Reduce (31) Statement. Pop 2 states. Push GOTO(72, Statement) = 72.
Shift 73
Reduce (84) Designator_Tail. Pop 0 states. Push GOTO(73, Designator_Tail) = 93.
Reduce (81) Designator. Pop 2 states. Push GOTO(72, Designator) = 69.
Shift 84
Reduce (61) Expr_Minus. Pop 0 states. Push GOTO(84, Expr_Minus) = 86.
Shift 111
Reduce (84) Designator_Tail. Pop 0 states. Push GOTO(111, Designator_Tail) = 149.
Reduce (81) Designator. Pop 2 states. Push GOTO(86, Designator) = 112.
Reduce (78) Factor_Designator. Pop 0 states. Push GOTO(112, Factor_Designator) = 151.
Reduce (72) Factor. Pop 2 states. Push GOTO(86, Factor) = 110.
Reduce (68) Term_Tail. Pop 0 states. Push GOTO(110, Term_Tail) = 146.
Reduce (66) Term. Pop 2 states. Push GOTO(86, Term) = 106.
Shift 137
Reduce (64) Addop. Pop 1 state. Push GOTO(106, Addop) = 139.
Shift 111
Reduce (84) Designator_Tail. Pop 0 states. Push GOTO(111, Designator_Tail) = 149.
Reduce (81) Designator. Pop 2 states. Push GOTO(139, Designator) = 112.
Reduce (78) Factor_Designator. Pop 0 states. Push GOTO(112, Factor_Designator) = 151.
Reduce (72) Factor. Pop 2 states. Push GOTO(139, Factor) = 110.
Reduce (68) Term_Tail. Pop 0 states. Push GOTO(110, Term_Tail) = 146.
Reduce (66) Term. Pop 2 states. Push GOTO(139, Term) = 201.
Reduce (63) Expr_Tail. Pop 0 states. Push GOTO(201, Expr_Tail) = 268.
Reduce (62) Expr_Tail. Pop 3 states. Push GOTO(106, Expr_Tail) = 140.
Reduce (59) Expr. Pop 3 states. Push GOTO(84, Expr) = 104.
Shift 136
Reduce (39) Statement_AssignOrCall. Pop 3 states. Push GOTO(69, Statement_AssignOrCall) = 82.
Reduce (31) Statement. Pop 2 states. Push GOTO(72, Statement) = 72.
Shift 77
Shift 97
Reduce (61) Expr_Minus. Pop 0 states. Push GOTO(97, Expr_Minus) = 101.
Shift 130
Reduce (84) Designator_Tail. Pop 0 states. Push GOTO(130, Designator_Tail) = 195.
Reduce (81) Designator. Pop 2 states. Push GOTO(101, Designator) = 131.
Reduce (78) Factor_Designator. Pop 0 states. Push GOTO(131, Factor_Designator) = 196.
Reduce (72) Factor. Pop 2 states. Push GOTO(101, Factor) = 129.
Reduce (68) Term_Tail. Pop 0 states. Push GOTO(129, Term_Tail) = 191.
Reduce (66) Term. Pop 2 states. Push GOTO(101, Term) = 126.
Reduce (63) Expr_Tail. Pop 0 states. Push GOTO(126, Expr_Tail) = 189.
Reduce (59) Expr. Pop 3 states. Push GOTO(97, Expr) = 123.
Reduce (46) Print_Opt. Pop 0 states. Push GOTO(123, Print_Opt) = 186.
Shift 248
Shift 304
Reduce (36) Statement. Pop 6 states. Push GOTO(72, Statement) = 72.
Reduce (30) Statements. Pop 0 states. Push GOTO(72, Statements) = 91.
Reduce (29) Statements. Pop 2 states. Push GOTO(72, Statements) = 91.
Reduce (29) Statements. Pop 2 states. Push GOTO(72, Statements) = 91.
Reduce (29) Statements. Pop 2 states. Push GOTO(72, Statements) = 91.
Reduce (29) Statements. Pop 2 states. Push GOTO(64, Statements) = 71.
Shift 90
Reduce (28) Block. Pop 3 states. Push GOTO(58, Block) = 63.
Reduce (17) MethodDecl. Pop 7 states. Push GOTO(13, MethodDecl) = 22.
Reduce (16) MethodDecls. Pop 0 states. Push GOTO(22, MethodDecls) = 31.
Reduce (15) MethodDecls. Pop 2 states. Push GOTO(13, MethodDecls) = 25.
Shift 33
Reduce (1) Program. Pop 6 states. Push GOTO(0, Program) = 2.
Accept
------------------------------------------------------------------------------
[SUCCESS] Canonical LR(1) Parser completed with 0 errors.

\end{verbatim}

\newpage
\section{Compiler Error Handling and Halt-on-Error Semantics}
The compiler implements strict validation rules where **compilation halts immediately at the first syntax or semantic error**. 
If the parser detects an invalid statement or mismatched token:
\begin{itemize}
    \item It raises an exception (`std::runtime_error`) inside the `reportError()` function.
    \item This prints the error details (with line/column coordinate lookup) and aborts the parser call stack.
    \item The console displays the successful parser output generated *prior* to the failure, ensuring clear visual separation between parsed structures and the error boundary.
\end{itemize}

\subsection{Error Handling Test Cases}
Below are 5 representative test cases demonstrating the error-handling output when syntax or semantic violations occur, showcasing compiler halts:

\begin{enumerate}
    \item \textbf{Test Case 1: Lexical Error (Invalid Symbol)}
    \begin{itemize}
        \item \textbf{Source Segment}: \texttt{int x \# 5;}
        \item \textbf{Behavior}: The double-buffered scanner encounters the invalid token \texttt{\#} and immediately reports:
        \begin{verbatim}
[LEXICAL ERROR] Line 3, Column 9: Unexpected character '#'
        \end{verbatim}
        \item \textbf{Halt}: Compiler execution aborts immediately, preventing further parsing.
    \end{itemize}

    \item \textbf{Test Case 2: Syntactic Error (Missing Semicolon)}
    \begin{itemize}
        \item \textbf{Source Segment}: \texttt{int x} (followed by \texttt{int y;})
        \item \textbf{Behavior}: The recursive descent and LL(1) parsers expect a semicolon to terminate the declaration block. They report:
        \begin{verbatim}
[SYNTAX ERROR] Line 4, Column 3: Expected ';' but found 'int'
        \end{verbatim}
        \item \textbf{Halt}: The parse stacks are cleaned up and the compilation is terminated.
    \end{itemize}

    \item \textbf{Test Case 3: Syntactic Error (Mismatched Parenthesis)}
    \begin{itemize}
        \item \textbf{Source Segment}: \texttt{while (x > 0 \{ x = x - 1; \}}
        \item \textbf{Behavior}: The parsers detect a missing closing parenthesis for the loop condition. They report:
        \begin{verbatim}
[SYNTAX ERROR] Line 12, Column 16: Expected ')' but found '{'
        \end{verbatim}
        \item \textbf{Halt}: Compiler execution is halted at the mismatched boundary.
    \end{itemize}

    \item \textbf{Test Case 4: Semantic Error (Duplicate Variable Declaration)}
    \begin{itemize}
        \item \textbf{Source Segment}: \texttt{int x; int x;}
        \item \textbf{Behavior}: The compiler successfully parses both declarations syntactically. However, during symbol table insertion, scope duplicate verification fails:
        \begin{verbatim}
[SEMANTIC ERROR] Line 4, Column 7: Redeclaration of identifier 'x' in scope 1
        \end{verbatim}
        \item \textbf{Halt}: Symbol table insertion triggers an immediate semantic halt.
    \end{itemize}

    \item \textbf{Test Case 5: Semantic Error (Undeclared Identifier Lookup)}
    \begin{itemize}
        \item \textbf{Source Segment}: \texttt{sum = x + z;} (where \texttt{z} was never declared)
        \item \textbf{Behavior}: During identifier resolution in the factor evaluation rules, the lookup inside the active symbol table stack returns null:
        \begin{verbatim}
[SEMANTIC ERROR] Line 10, Column 13: Identifier 'z' is undeclared in this scope
        \end{verbatim}
        \item \textbf{Halt}: The compiler halts immediately to prevent invalid type check cascades.
    \end{itemize}
\end{enumerate}



\section{Conclusion}
This compiler playground combines a modular C++ validating core with a responsive sandbox. The integration of five compiling layers—synchronized to halt immediately on syntax failures—guarantees correct, deterministic evaluation of MicroJava code files, serving as an effective practical platform for syntax analysis.

\end{document}
